---
title             : "Is there really such a thing as _Tropical_ Biology?^[Inspired by the provocative title of an essay by M. H. Robinson.]"
shorttitle        : "LRH: Bruna /nRRH: On Tropical Biology"

author: 
  - name          : "Emilio M. Bruna"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Wildlife Ecology and Conservation, University of Florida, PO Box 110430, Gainesville, FL 32611-0430, USA"
    email         : "embruna@ufl.edu"
    role: # Contributorship roles (e.g., CRediT, https://credit.niso.org/)
      - Methodology
      - Data curation
      - Investigation
      - Conceptualization
      - Formal analysis
      - Project administration
      - Resources
      - Software
      - Validation
      - Visualization
      - Writing – original draft
      
affiliation:
  - id            : "1"
    institution   : "Department of Wildlife Ecology and Conservation, University of Florida, PO Box 110430, Gainesville, FL 32611-0430, USA"
  - id            : "2"
    institution   : "Center for Latin American Studies, University of Florida, PO Box 115530, Gainesville, FL 32611-5530, USA"

authornote: |
  
  Received:______; Revised:______; Accepted:______.  
  
  \bigskip
  
keywords          : "up to eight"
wordcount         : "X"
bibliography      : "ATBC_2022_Plenary.bib"
nocite: |
  @ripleyPerspectivesTropicalBiology1967, @janzenWhitherTropicalEcology1972, @richardsNeedDevelopmentTropical1946,@richardsWhatTropicsCan1963, @richardsProgrammeTropicalBiology1964, @webbBiologyTropics1960, @robinson1978tropical
floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no
figurelist        : no
tablelist         : no
footnotelist      : no
classoption       : "man, donotrepeattitle" # suppresses title on 1st page of MSoutput            "
appendix: "./manuscript/bruna_supplement.Rmd"
# output            : papaja::apa6_pdf
output:
  papaja::apa6_pdf:
  keep_tex: true   
mainfont: Times New Roman
fontsize: 12pt
csl: "biotropica.csl"
fig_caption: yes
always_allow_html: yes
# keep_tex: yes
header-includes:
  - \usepackage{fancyhdr}
  - \pagestyle{empty} # this supresses running head on title page along with next
  - \thispagestyle{empty} # this supresses running head 
  - \pagestyle{fancy} # now can add the headers on subsequent pages
  - \fancyfoot[C]{\thepage} # remove page number bottom of the page
  - \fancyhead[L]{Bruna}
  - \fancyhead[R]{ATBC Presidential Plenary}
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \usepackage{setspace} # line spacing
  - \raggedbottom
 # - \usepackage{endfloat} #[nomarkers] excludes the {insert figure x around here] from main text. The others exclude the list of tables and figures. https://cs.brown.edu/about/system/managed/latex/doc/endfloat.pdf
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage{parskip}
  - \setlength{\parskip}{0pt}
  - \setlength\parindent{22pt}
---


```{r GlobalOptions, include=FALSE}
# options(knitr.duplicate.label = 'allow')
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
options(knitr.table.format = "latex")
options(knitr.duplicate.label = 'allow',
        knitr.kable.NA = '')
knitr::opts_knit$set(eval.after = "fig.cap")
# knitr::opts_chunk$set(fig.pos = 'h')
```


```{r setup, include = FALSE}
library("papaja")
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(knitr)
library(cowplot)
library(here)
# library(egg)
library(magick)
# library(citr)
# library(devtools)
# devtools::install_github("crsh/papaja")
# devtools::install_github("haozhu233/kableExtra")
r_refs("biotropica.csl")
library(stopwords)
# library(ngram)
library(tidytext)
library(janitor)

```




```{r tableVars, cache=TRUE, echo = FALSE,message=FALSE,warning=FALSE}

cutoff=75
start_yr<-1990
end_yr<-2022


system <- c(
  "mammal",
  "usa",
  "grassland",
  "tropical forest",
  "panama",
  "costa rica",
  "liana",
  "litter",
  "seedling",
  "forest",
  "tree",
  "tropical wet forest",
  "zooplankton",
  "dipterocarpaceae",
  "tropical rainforest",
  "bci",
  "bird",
  "drosophila melanogaster",
  "brazil",
  "mexico",
  "tropical dryforest",
  "borneo",
  "cerrado",
  "ecuador",
  "cloud forest",
  "drosophila",
  "drosophila melanogaster",
  "ant",
  "epiphyte",
  "amazonia",
  "secondary forest",
  "tropic",
  "elephant",
  "chiroptera",
  "rodent",
  "colombia",
  "atlantic forest",
  "rainforest",
  "puerto rico",
  "savanna",
  "africa",
  "neotropic",
  "amazon",
  "usa",
  "tanzania",
  "malaysia",
  "french guiana",
  "hawaii",
  "peru",
  "australia",
  "amphibian",
  "lepidoptera",
  "venezuela",
  "andes",
  "bats",
  "formicidae",
  "la selva",
  "mangrove",
  "india",
  "primate",
  "bolivia",
  "anuran",
  "madagascar",
  "indonesia", 
  "reptile",
  "caribbean",
  "kenya",
  "ficus",
  "hummingbird",
  "african",
  "pacific"
  )

system <- as_tibble(system)


system_bigrams<-c(
"drosophila melanogaster",
"north american",
"salt marsh",
"british isles" ,
"north america",
"drosophila pseudoobscura",
"boreal forest",
"tropical forest",
"tropical rainforest",
"dry forest",
"national park", 
"tropical dry",
"atlantic forest", 
"tropical tree",
"puerto rico",
"cloud forest",
"coral reef",
"tropical montane",
"deciduous forest",
"rainforest tree",
"african savanna",
"neotropical forest",
"pacific coast",   
"dung beetle",
"veracruz mexico",
"wet forest",  
"amazonian forest",
"lowland tropical",
"french guiana",   
"western ghats",   
"brazilian atlantic",  
"dry tropical",
"lowland rainforest",  
"evergreen forest",
"baja california", 
"cutting ant",
"nicoya costarica",
"ant plant",  
"litter decomposition",
"montane rainforest",
"montane forest",
"hymenoptera formicidae",
"mangrove forest",
"sea urchin",
"california mexico",
"dipterocarp forest",
"central amazonia", 
"chiapas mexico",  
"eastern pacific", 
"southeastern brazil",
"neotropical rainforest",  
"arbuscular mycorrhizal", 
"lowland forest",  
"tree community",
"colombian caribbean", 
"tropical wet",
"bird community",
"ghats india", 
"golfo dulce",
"park costarica",
"south eastern"
)

# Journals

title<-c("Journal of Evolutionary Biology",
          "Ecology",
          "Journal of Applied Ecology",
          "Evolution", 
          "Biotropica",
          "Journal of Ecology",
          "Tropical Conservation Science",
          "American Naturalist",
          "Tropical Ecology",
          "Journal of Tropical Ecology",
          "Revista de Biologia Tropical")
 
SO<-c("jeb", 
         "ecology",
         "jae",
         "evol",
         "bitr",
         "jecol",
         "tcs",
         "amnat",
         "trec",
         "jte",
         "rbt")

  jrnl_cat<-c("general", 
         "general",
         "general",
         "general",
         "tropical",
         "general",
         "tropical",
         "general",
         "tropical",
         "tropical",
         "tropical")
 
titles<-tibble(title,SO,jrnl_cat) 

# EXCLUDE JOURNALS FROM ANALYSIS HERE

titles_analyzed<-titles %>% 
 filter(SO!="rbt") %>%
  filter(SO!="jeb") %>% 
  filter(SO!="evol") 


system_bigrams <- as_tibble(system_bigrams) 

system<-bind_rows(system,system_bigrams)



```

\onehalfspacing
\singlespacing


## 1. INTRODUCTION

\noindent _"This is an interesting and useful study, but I feel the manuscript is better suited to a specialized journal focusing on tropical ecosystems."_  

`r tufte::quote_footer('Subject Editor _(name and journal redacted)_')`


\bigskip

\noindent This decision regarding my submission to one of our field's well-known journals is likely familiar to many members of the Association for Tropical Biology & Conservation (ATBC). All three reviews were positive, with none of the referees identifying significant shortcomings or requesting major changes. So why had the manuscript been rejected? My only clue was in the Editor's conclusion, from which I gathered they felt studies done _in_ the tropics were of limited relevance to researchers working _outside_ the tropics. That's for whom a specialized journal is published, after all -- a smaller community of subject-matter experts -- and the journal to which we had submitted our study sought to publish "broad conceptual advances".  In short, the Subject Editor was drawing a distinction between _Biology_ and _Tropical_ Biology, with the latter a specialized subdiscipline of the former.  
   This limited view of tropical research is not new. In 1963, P. W. Richards felt it necessary to use his Presidential Address to the British Ecological Society to explain "what the Tropics can contribute to ecology", advocate for the tropics to be studied more intensively, and to encourage students to visit "the most [biologically] exciting part of the world" [@richardsWhatTropicsCan1963]. His reason for choosing this topic, while self-deprecating, was pointed - he was concerned that a overview of his own research or recent advances in tropical ecology "would probably bore the large part of my audience." [@richardsWhatTropicsCan1963]. That he felt doing so was necessary despite he and others having done so for decades [@huxleyEditorIntroduction1927;@chapmanNeedDevelopmentTropical1945; @richardsNeedDevelopmentTropical1946; @parkObservationsConcerningFuture1945] was surely frustrating.   
   Sixty years on many of us find ourselves similarly frustrated. Field stations in the tropics remain underfunded [@cornerNeedDevelopmentTropical1946; @eppleyTropicalFieldStations2024]. Financial support for tropical research continues to decline [@chapmanNeedDevelopmentTropical1945; @sohmerNSFSupportBasic1980; @stegmannBrazilianPublicFunding2024]. And despite the tropics comprising the majority of the planet's biodiversity [@gastonGlobalPatternsBiodiversity2000], ~40% of its terrestrial surface area, and half the human population [@hoornwegPopulationPredictionsWorld2017], the study of tropical systems is still viewed by many as a specialization. My objective in this essay is not to review the historical origins [e.g., @chazdonFoundationsTropicalForest2001; @raby2017american] or consequences [@zukTemperateAssumptionsHow2016] of this generalization, the subsequent proposals to advance tropical research [@janzenWhitherTropicalEcology1972; @janzenFutureTropicalEcology1986; @robinson1978tropical; @bawaParadiseMeetingChallenges2004; @buechnerContributionWorldProgram1967; @richardsProgrammeTropicalBiology1964], or the ensuing and often contentious debates about latitudinal gradients in biological processes [@molesNotionThatSpecies2016; @robinson1978tropical]. Instead, I will try to address the long-standing and fundamental -- but to date inexplicably untested -- assumption underpinning the Editor's recommendation: Is there really such a thing as _Tropical_ Biology?

## 1. Why the answer is *'No'.*

\noindent _"In attempting to study vegetation and to arrive at generalizations...it would be more logical to begin with the floristically rich vegetation of the tropics than, as we now do, with the impoverished vegetation of northern Europe and North America."_

`r tufte::quote_footer('P. W. Richards (1946)')`
\bigskip


<!-- > _"The science of ecology developed first in central Europe, Scandinavia and Britain and very slightly later in the United States. The ideas and concepts with which it started were therefore inevitably based on the conditions in a temperate climate..."_  -->
<!-- `r tufte::quote_footer('P. W. Richards (1963)')` -->
<!-- \bigskip -->

<!-- >_"In what way will a more intensive study of ecology in the tropics be likely to alter our present ecological ideas? In other words what can the tropics contribute to ecology?"_ -->
<!-- <!-- `r tufte::quote_footer('P. W. Richards (1963)')` --> 
<!-- <!-- \bigskip --> 


<!-- > _"...in the case of biology, a major part of the accumulated biological knowledge is concerned with a rather minor part of the world's fauna and flora, because of the chance development of biology in the temperate zones."_   -->

<!-- `r tufte::quote_footer('S. D. Ripley (1967)')` -->
<!-- \bigskip -->

\noindent One means of assessing if _Tropical_ Biology is a distinct academic discipline is by considering the communities into which scientists self-organize. Scholarly societies are one such community; their establishment requires both an intellectual pursuit with which individuals identify and a critical mass of like-minded individuals in search of community. Some of these communities coalesce around broad conceptual domains (e.g., _Evolutionary_ Biology, _Conservation_ Biology, _Integrative_ Biology; Figure \@ref(fig:fig-org)A). Still others bring together individuals from different conceptual domains that share an interest in a particular system (e.g., _Avian_ Biology, _Island_ Biology; Figure \@ref(fig:fig-org)B). Finally, some scholarly societies comprise individuals grounded in a common methodological framework, though they may do so with disparate study systems or to address questions in distinct conceptual domains (e.g., _Molecular_ Biology, _Mathematical_ Biology, _Systematic_ Biology; Figure \@ref(fig:fig-org)C).   
    _Tropical_ Biology fails to align with any of these constructs. Its practitioners investigate fundamental questions across conceptual domains with a broad range of methodological approaches and study systems. Even the adjective that would seem be a unifying thread is challenging to operationalize. 'The Tropics' are geographically defined as the portion of the Earth's surface receiving at least one day of direct overhead sunlight per year --- a band delineated by the Tropics of Capricorn (23°26'10.4" S) and Cancer (23°26'10.4" N). However, the ranges of many 'tropical' species extend far beyond these boundaries^[Perhaps the most extreme examples are migratory birds such as the northern wheatear (_Oenanthe oenanthe_), which fly over 14,000 km from sub-Saharan Africa to their breeding grounds in the Arctic [@bairleinCrosshemisphereMigration252012]], and a review by @feeleyWhereEarthAre2018 of over 200 scientific articles identified at least eight distinct criteria by which authors defined 'tropical' systems. How then is it that _Tropical Biology_ come to be seen as a distinct subdicipline despite the lack the sharp boundaries around which scientific groups typically coalesce?  
    These contemporary perceptions of 'The Tropics' as distant and different are the result of centuries of historical and cultural reinforcement [@driverConstructingTropicsIntroduction2000; @arnold1996problem; @miller2011visions; @stepan2001picturing; @miller2011visions]. The first Europeans to visit the tropics returned with vivid, captivating, and frequently pejorative descriptions of the places and people they encountered [@inbook]. Their stories and images established a series of persistent, often contradictory tropes about tropical regions and people that were then repeated and reinterpreted by subsequent visitors [@stepan2001picturing; @smithEuropeanVisionSouth1950]. The historian David Arnold has argued that these narratives of _Tropicality_ [_sensu_ @alma9913280634202441], and even referring to this part of the globe as _The Tropics_, allowed Europeans simultaneously define the region as environmentally and culturally distinct while also superimposing a common identity on very distinct parts of the tropical world [@arnold1996problem].   
   The view of the tropics as simultanously 'exotic' and 'other' was prevalent during the formative years of von Humboldt, Darwin, and Wallace. Those they inspired that went on to formalize the fields of ecology and evolution, almost all of whom were based in Europe or North America, also grew up immersed in stereotypes about the tropics. They were obviously not ignorant about these locations and their biology, and many considered a trip to the tropics an essential rite of passage for their students [@webbBiologyTropics1960]. Others went even further --- in in his 1945 Presidential Address to the Ecological Society of America, Orlando Park impressed upon his audience the importance of the tropics and encouraged ESA to establish a "full scale program in tropical ecology" and consider establishing "a new journal...dealing with tropical biology in its broadest aspects" [@parkObservationsConcerningFuture1945]. But given that many of the scientists that Park and Richards were addressing "have never been to the tropics and never intend to do so" [@richardsWhatTropicsCan1963], and how the biology of the tropics quickly overwhelmed paradigms and theory developed to explain temperate patterns [@cornerNeedDevelopmentTropical1946; @richardsProgrammeTropicalBiology1964; @richardsNeedDevelopmentTropical1946; @richardsWhatTropicsCan1963], one can understand how the notion that the tropics were _culturally_ unique gave rise to the scientific generalization that the tropics were _biologically_ unique. 

## 2. Why the answer is *'Maybe'.*

```{r biblio, include = FALSE,echo = FALSE,message=FALSE,warning=FALSE}
# load data ---------------------------------------------------------------

# kw<-read_csv(here("bibliometrics","data_clean","keywords.csv")) %>% 
#  filter(SO!="rbt") 
# %>%
#   filter(SO!="trec") 
kw<-read_csv(here("bibliometrics","data_clean","keywords.csv")) %>% 
  inner_join(titles_analyzed) %>% 
  relocate(title,.after=SO) %>% 
  mutate(title=as.factor(title))

kw<-kw %>% 
  filter(PY>=start_yr) %>% 
  filter(PY<=end_yr)


# N of keywords
n_kw<-kw %>% summarize(n=n_distinct(final))

# N of publications
n_pubs<-kw %>% summarize(n=n_distinct(refID)) 
n_pubs_trop<-kw %>% filter(pub_cat_2=="tropical") %>% summarize(n=n_distinct(refID)) 
n_pubs_gen<-kw %>% filter(pub_cat_2=="general") %>% summarize(n=n_distinct(refID)) 

# N of journals
library(xfun)
n_jrnls<-kw %>% select(SO) %>% summarize(n=n_distinct(SO)) 
n_jrnls_trop<-kw %>% filter(jrnl_cat=="tropical") %>% summarize(n=n_distinct(SO)) %>% mutate(n=numbers_to_words(n))
n_jrnls_gen<-kw %>% filter(jrnl_cat=="general") %>% summarize(n=n_distinct(SO)) %>% mutate(n=numbers_to_words(n))

# time frame: 
yr_last<-kw %>% select(PY) %>% max() 
yr_first<-kw %>% select(PY) %>% min() 

titles_string<-titles_analyzed %>% 
  select(-jrnl_cat) %>% 
  pivot_wider(names_from = SO, values_from = title) 
titles_string<-titles_string %>%  unite(titles_string,1:ncol(titles_string),sep=", ")

titles_trop<-titles_analyzed %>% filter(jrnl_cat=="tropical")
trop_titles_string<-titles_trop %>% 
  filter(jrnl_cat=="tropical") %>% 
  select(-jrnl_cat) %>% 
  pivot_wider(names_from = SO, values_from = title) 
trop_titles_string<- trop_titles_string %>%
  unite(titles_trop,1:ncol(trop_titles_string),sep=", ")


# What % of articles in GENERAL Journals are tropical

perc_trop <- kw %>%
  group_by(jrnl_cat, pub_cat_2, SO) %>%
  summarise(n_pubs = n_distinct(refID)) %>%
  ungroup() %>%
  arrange(jrnl_cat, SO, pub_cat_2, desc(n_pubs)) %>% 
  filter(jrnl_cat=="general") %>% 
  pivot_wider(
    names_from = pub_cat_2,
    values_from = n_pubs) %>% 
  mutate(perc_trop=tropical/(general+tropical)*100)


overall_perc_trop<-((sum(perc_trop$tropical))/sum(perc_trop$general))*100
avg_perc_trop<-mean(perc_trop$perc_trop)
var_perc_trop<-sd(perc_trop$perc_trop)


# What % of articles have the top N words? 

# inner_join(kw,in_both_kw,by="final") %>% summarize(n_distinct(refID))
# ~26000 of 36963 articles
# 70% of articles!

# TITLE WORDS

tw_all<-read_csv(here("bibliometrics","data_clean","tw_clean.csv")) %>% 
  inner_join(titles_analyzed) %>% 
  relocate(title,.after=SO) %>% 
  mutate(title=as.factor(title)) %>% 
  mutate(pub_cat=as.factor(pub_cat_2)) %>% 
  mutate(jrnl_cat=as.factor(jrnl_cat)) %>% 
  mutate(index = row_number()) %>% 
  mutate(pub_cat_2=as.factor(pub_cat_2))

tw_all<-tw_all %>% 
  filter(PY>=start_yr) %>% 
  filter(PY<=end_yr)

n_tw<-tw_all %>% summarize(n=n_distinct(final))

# Keywords that are "system"

pubs_per_pub_cat <- kw %>%
  group_by(pub_cat_2) %>%
  summarise(n_pubs = n_distinct(refID)) %>%
  ungroup() %>%
  arrange(pub_cat_2, desc(n_pubs))


top_kw<- kw %>% 
  group_by(pub_cat_2, final) %>%
  tally() %>%
  arrange(pub_cat_2, desc(n)) %>%
  group_by(pub_cat_2) %>%
  arrange(pub_cat_2, desc(n)) %>%
  left_join(pubs_per_pub_cat) %>%
  group_by(pub_cat_2) %>%
  mutate(perc_pubs_wth_kw = (n / n_pubs * 100)) %>%
  group_by(pub_cat_2) %>%
  arrange(pub_cat_2, desc(n)) %>%
  mutate(rank_perc = rank(desc(n),  ties.method = c("random"))) %>%
  # mutate(rank_perc = min_rank(desc(n))) %>%
  # arrange(rank_perc,jrnl_cat,desc(pub_cat_2))
  arrange(desc(pub_cat_2),rank_perc) %>% 
  mutate(system = if_else((final %in% system$value == TRUE), "Y", "N")) %>%
  mutate(system = as.factor(system)) %>% 
  filter(rank_perc<=cutoff) 

trop_system<-top_kw %>% 
  group_by(pub_cat_2,system) %>% 
  tally() %>% 
  mutate(perc_system=n/cutoff*100) %>% 
  filter(system=="Y") %>% 
  filter(pub_cat_2=="tropical") %>% 
  ungroup() %>% 
  select(perc_system)


nontrop_system<-top_kw %>% 
  group_by(pub_cat_2,system) %>% 
  tally() %>% 
  mutate(perc_system=n/cutoff*100) %>% 
  filter(system=="Y") %>% 
  filter(pub_cat_2=="general") %>% 
  ungroup() %>% 
  select(perc_system)

# BIGRAMS


# NGRAMS

extract_ngram_data <- function(tw) {
  ngram_data<-tw_all %>% 
    select(refID,PY,SO,pub_cat_2,jrnl_cat,final) %>%  
    arrange(refID,PY,SO) %>% 
    group_by(refID,PY,SO) %>% mutate(word=row_number()) %>% 
    relocate(word,.before=final) %>% 
    mutate(place="place") %>% 
    relocate(place,.before=word) 
  # %>% 
  #   replace_na(list(final="-"))
  ngram_data<-ngram_data %>% replace_na(list(final= "deleteme")) %>% 
    pivot_wider(names_from = c(place,word),
                values_from = final,
                values_fn = list, values_fill = list("deleteme")
    ) %>%
    ungroup()
  
  last_col<-ngram_data %>% select(last_col())
  last_col<-last(names(ngram_data))
  ngram_data<- ngram_data %>% 
    unite("tw", place_1:last_col, na.rm = FALSE, remove = TRUE, sep= " ") %>% 
    ungroup()
  return(ngram_data)
}

ngram_data<-extract_ngram_data(tw_all)
ngram_data

# ngram_data_trop<-ngram_data %>% filter(jrnl_cat=="tropical")
# ngram_data_gen_gen<-ngram_data %>% filter(jrnl_cat=="general" & pub_cat_2=="general")
# ngram_data_gen_trop<-ngram_data %>% filter(jrnl_cat=="general" & pub_cat_2=="tropical")

ngram_data_gen<-ngram_data %>% filter(pub_cat_2=="general")
ngram_data_trop<-ngram_data %>% filter(pub_cat_2=="tropical")


# ngrams -----------------------------------------------------------------


# to do by cat filter first

generate_bigrams <- function(ngram_data) {
  tw_bigrams <- ngram_data %>% 
    select(tw) %>% 
    # slice(1:100) %>% 
    unnest_tokens(bigram, tw, token = "ngrams", n = 2) %>% 
    count(bigram, sort = TRUE) 
  bigrams_separated <- tw_bigrams %>% 
    separate(bigram, c("word1", "word2"), sep = " ")
  bigrams_filtered <- bigrams_separated  %>%
    filter(!word1 %in% stop_words$word) %>%
    filter(!word2 %in% stop_words$word) %>% 
    arrange(desc(n)) %>% 
    filter(str_detect("deleteme",word1,negate=TRUE)) %>% 
    filter(str_detect("deleteme",word2,negate=TRUE)) 
    # slice(1:1000)
    
    
  bigrams_filtered<-bigrams_filtered %>% 
    # filter(nchar(word1)<4) %>%
    mutate(word1_first=substring(word1, 1, 1)) %>% 
    mutate(word2_first=substring(word2, 1, 1)) %>% 
    mutate(number=case_when(
      (str_detect(word1_first,".*[0-9].*")) == TRUE ~ "number",
      (str_detect(word2_first,".*[0-9].*")) == TRUE ~ "number",
      TRUE ~ "keep")) %>% 
    filter(number=="keep") %>% 
    select(-number,-word1_first,-word2_first) %>% 
    mutate(perc=n/sum(n)*100)
  return(bigrams_filtered)
}

  
  # bigrams as % of titles

generate_bigrams <- function(ngram_data) {
  
  n_titles<-ngram_data %>% summarize(n=n_distinct(refID))
  
  tw_bigrams <- ngram_data %>% 
    select(tw,refID) %>% 
    # slice(1:100) %>% 
    unnest_tokens(bigram, tw, token = "ngrams", n = 2) %>% 
    distinct(refID,bigram)
  
  # %>% 
  #   count(refID,bigram, sort = TRUE)
  bigrams_separated <- tw_bigrams %>% 
    separate(bigram, c("word1", "word2"), sep = " ")
  bigrams_filtered <- bigrams_separated  %>%
    filter(!word1 %in% stop_words$word) %>%
    filter(!word2 %in% stop_words$word) %>% 
    # arrange(desc(n)) %>% 
    filter(str_detect("deleteme",word1,negate=TRUE)) %>% 
    filter(str_detect("deleteme",word2,negate=TRUE)) 
  # slice(1:1000)
  
  
  bigrams_filtered<-bigrams_filtered %>% 
    # filter(nchar(word1)<4) %>%
    mutate(word1_first=substring(word1, 1, 1)) %>% 
    mutate(word2_first=substring(word2, 1, 1)) %>% 
    mutate(number=case_when(
      (str_detect(word1_first,".*[0-9].*")) == TRUE ~ "number",
      (str_detect(word2_first,".*[0-9].*")) == TRUE ~ "number",
      TRUE ~ "keep")) %>% 
    filter(number=="keep") %>% 
    select(-number,-word1_first,-word2_first)  %>% 
    group_by(word1,word2) %>% 
    summarize(n=n()) %>% 
    arrange(desc(n)) %>% 
    mutate(perc=n/n_titles$n*100)
  return(bigrams_filtered)
}



bigrams<-generate_bigrams(ngram_data)  

bigrams_count<- bigrams %>% 
  unite("bigram",word1:word2, sep = " ") %>% 
  tally()


# bigrams_count<-read_csv("./bibliometrics/data_clean/bigrams_count.csv")
bigrams_count<-bigrams_count %>% as.numeric()



NonTrop_bigrams<-generate_bigrams(ngram_data_gen) %>% 
  mutate(cat="non-tropical") 

Trop_bigrams<-generate_bigrams(ngram_data_trop) %>% 
  mutate(cat="tropical") 


NonTrop_bigrams<-NonTrop_bigrams %>%  
  mutate(bigram=paste(word1,word2,sep=" ")) %>% 
  ungroup() %>% 
  mutate(rank_perc = rank(desc(perc), ties.method = "random")) 
# %>%
#   mutate(bigram = paste(bigram, " (", rank_perc, ")", sep = "")) 

Trop_bigrams<-Trop_bigrams %>% 
  mutate(bigram=paste(word1,word2,sep=" ")) %>% 
  ungroup() %>% 
  mutate(rank_perc = rank(desc(perc), ties.method = "random")) 




system<-bind_rows(system_bigrams,system)


rankings_pub<-bind_rows(Trop_bigrams,NonTrop_bigrams)

rankings_pub <- rankings_pub %>%
  mutate(system = if_else((bigram %in% system$value == TRUE), "Y", "N")) %>%
  mutate(system = as.factor(system)) %>% 
  group_by(cat) %>% 
  mutate(rank_perc = rank(desc(perc), ties.method = "random")) %>% 
  filter(rank_perc<=50) 

in_both <- rankings_pub %>%
  group_by(bigram) %>%
  summarise(n2 = n()) %>%
  filter(n2 > 1) %>%
  mutate(both = TRUE)

plot_tw <- full_join(rankings_pub, in_both, by = "bigram") %>% 
  select(-n2) %>% 
  replace_na(list(
    "both" = FALSE
  )) %>% 
group_by(cat) %>%
  arrange(cat, desc(n)) %>%
  mutate(rank_perc = rank(desc(n),  ties.method = c("random"))) 
  

```


\noindent _"...to this day ecology is biased by concepts and ideas appropriate mainly to the study of vegetation in temperate climate."_

`r tufte::quote_footer('P. W. Richards (1963)')`
\bigskip

<!-- > _"It is also evident that much of our current teaching in ecology, as well as in other branches of biology, would be set in a truer perspective if more consideration were given to tropical vegetation and the conditions...in the tropics."_ -->
<!-- `r tufte::quote_footer('P. W. Richards (1946)')` -->
<!-- \bigskip -->


\noindent Even if 'The Tropics' are a historical construct, _Tropical Biology_ could still be conceptually distinct field of study if, over time, the scientific community converged on a suite of topics either unique to or best studied in tropical systems. To assess this possibility, I used text-mining tools to compare the content of `r scales::comma(as.numeric(n_pubs_trop))` articles reporting research from the tropics with `r scales::comma(as.numeric(n_pubs_gen))` studies conducted in other parts of the world. These studies were published from `r (as.numeric(start_yr))`-`r (as.numeric(end_yr))` in N = `r n_jrnls` journals (_`r titles_string`_).  
    A complete description of the methods used to gather and process these data are in the _Supplementary Materials_. Briefly, I began by extracting all keywords, title words (e.g., _seed_, _species_), and title bigrams (i.e., pairs of sequential words, e.g., _seed predation_, _species diversity_) from the entire collection of articles; this resulted in N = `r scales::comma(as.numeric(n_kw))` keywords, N= `r scales::comma(as.numeric(n_tw))` title words, and N = `r scales::comma(as.numeric(bigrams_count))` bigrams. I then calculated the percentage of articles in each category using each of those terms. The results below are based on the top N = `r cutoff` terms in each article category. 
    Two major patterns emerge from this analysis. The first is that `r scales::comma(as.numeric(trop_system))`% of the most frequently used keywords from 'tropical' articles were study systems or geographic locations (e.g., _Costa Rica_, _Amazonia_, _bats_). In contrast, the overwhelming majority of keywords from non-tropical articles (`r scales::comma(as.numeric(100-nontrop_system))`%) were conceptual (e.g., _competiton_, _ecosystem function_, _sexual selection_; Table \@ref(tab:kwtable)). The second is that after removing the system- and location-specific keywords, there is ample conceptual overlap between tropical and non-tropical studies (Table \@ref(tab:kwtableNosystem)) that is consistent with broader trends in ecological research [@carmelTrendsEcologicalResearch2013; @andersonTrendsEcologyConservation2021; @mccallenTrendsEcologyShifts2019]. That said, the most common research topics within each article category often differ dramatically in their relative rankings (Figure \@ref(fig:keywords)), and there are notable areas of topical divergence (Table \@ref(tab:kwtableNosystem)). Similar patterns emerge when comparing individual title words and title word bi-grams (Figure \@ref(fig:titlewords), Figure \@ref(fig:bigrams)).  
   One interpretation of these results is that _Tropical_ Biology is indeed a subdiscipline focused on problems and topics unique to or most relevant in tropical locations, and it is undoubtedly true that there are some questions best addressed in or relevant to tropical ecosystems. However, the observed differences could also reflect the historical relegation of certain academic subjects to the tropics, which is then reinforcing by "temperate biases" [_sensu_ @zukTemperateAssumptionsHow2016] or the overrepresentation of certain research sites [@stocksGeographicalInstitutionalDistribution2008], all of which can shape the development of theory and determine what data are used to test it [@raby2017american]. A similar argument has been put forward for the social sciences by @castrotorresNorthSouthNaming2022, who argue that the far greater prevalence of geographic markers in the titles of articles by authors in the Global South both indicates and perpetuates "an unwarranted claim on universality" by scholars from North America and Europe. This parallel evidence from a different field is compelling; nevertheless, the patterns presented here are insufficient for affirming the intellectual independence of _Tropical_ Biology.


## 3. Why the answer is *'Yes'.*

\noindent _"No education complete without trip to the Tropics."_ 

`r tufte::quote_footer('J. E. Webb (1960)')`

\bigskip
<!-- >_In what way will a more intensive study of ecology in the tropics be likely to alter our present ecological ideas? In other words what can the tropics contribute to ecology?_ -->

<!-- `r tufte::quote_footer('P. W. Richards (1963)')` -->


<!-- \bigskip -->

\noindent Finally, I believe an argument can be made for treating _Tropical Biology_ as a unique discipline, but not one based on the reasons typically put forward by others. What sets _Tropical Biology_ apart is not the biology _per se_ [_sensu_ @robinson1978tropical]. Rather, what Tropical Biologists have in common is the broader context in which their scholarship is embedded and carried out. Research anywhere is challenging, but for tropical biologists the precarious infrastructure, economic volatility, limited resources, and political instability can make the challenges feel insurmountable. These struggles can be compounded by having to communicate one's results in a foreign language [@amanoLanguagesAreStill2016] to the potentially biased reviewers and readers [@smithPeerReviewPerpetuates2023] of journals that are increasingly charging publications fees equivalent to several months salary [@smithAssessingEffectArticle2021]. When added to the physical and emotional toll of disease, crime, working in isolation, habitat loss, and the potential for professional retribution or physical violence [@clancySurveyAcademicField2014; @ellwangerDiversityLossClimate2020; @palinkasGlobalClimateChange2020], tropical biology and conservation can be uniquely dangerous --- even deadly. Lamentably, this is also true for the heroic conservationists, indigenous leaders, and journalists with whom we work [@cavalcantiPoliticalViolenceMobilisation2023].

## 4. The Future of (Tropical) Biology

_"There are few things more presumptuous than a US scientist holding forth on the future of tropical ecology"_  

`r tufte::quote_footer('D. H. Janzen (1972)')` 

\bigskip

<!-- > _"It would be presumptious for any one group of biologists, and still more for any individual, to attempt to write a programme for tropical biology"_ -->

<!-- `r tufte::quote_footer('P. W. Richards (1964)')`  -->

<!-- \bigskip -->

\noindent What if the scientific community had paid heed to @richardsNeedDevelopmentTropical1946 and properly centered the tropics when drawing biological generalizations? Perhaps Universities in Europe and North America would offer elective courses in "Temperate Biology". The instructors of these courses might present their research at the annual meeting of the _Association for Temperate Biology & Conservation_ (Figure \@ref(fig:fig-temp)) and publish papers in specialized journals, with article titles that --- in contrast to the more broadly relevant research from the tropics --- emphasize the systems or locations the work was done (Figure \@ref(fig:fig-pubs)).  
<!-- if only could find sonfg lyriuc about not worth reliving the past -->
    I prefer instead to consider what the ambiguity of my conclusions implies for how we should move forward. I suggest that the future of lies in neither dropping the adjective that motivates so many of us, nor keeping it and accepting status as as specialization. Instead, I call on ATBC members to **_reclaim and reshape the Tropical Narrative_:** to continue taking pride and elevating what makes biology in the tropics distinct and important --- the places and context in which we work --- while also working to properly recenter tropical ecosystems as the foundation of Biology and focus of conceptual attention. Below are six actions with which I propose anyone can contribute to this movement.  

**_Cite with purpose._** Citation is a powerful and political act; it conveys legitimacy on the scholarship in the article being cited as well as its author, helps elevate the profile of the author and study system, and those reading your work will cite these articles when writing their own. For many scientists it also plays an important role in their professional advancement. Be mindful of this impact and the opportunity it presents when choosing whom to cite. Cite scientists whose work or approach you feel is undervalued or overlooked. Cite scientists from countries or institutions that have been ignored by the broader scientific community. Cite scientists whose approach to research you feel others should emulate. Cite studies conducted in the tropics.  

**_Teach with Purpose._** All tropical biologists are teachers, whether it be in a classroom or in a meeting with policy makers, and teaching also provides an opportunity to elevate the scholarship of others. Be mindful of whose papers are assigned as readings, the studies and systems used to illustrate concepts, and the scientists highlighted in presentations. Use your syllabus as a tool to recast the narrative about the tropics and the scientific community that studies them. Train students in the skills needed when working in tropical systems --- collaboration, facilitation, conflict resolution, and communication to diverse audiences [@kainerGraduateEducationFramework2006; @duchelleGraduateStudentsKnowledge2009]. Teach collaboratively and cross-nationally [@russellIntegratingTropicalResearch2022].

**_Collaborate with Purpose._**  International collaboration can be challenging, but personally and professionally rewarding [@smithScientificImpactNations2014]. Be mindful of global scientific inequities, laws, and 'parachute science' [@ramirez-castanedaSetPrinciplesPractical2022; @gomez-pompaRoleBiodiversityScientists2004; @asaseReplacingParachuteScience2022]. Allow community members to guide the development of research priorities and questions [@kainerPartneringGreaterSuccess2009]. Push for organizations to strengthen collaborations with --- and especially within --- the Global South [@ocampo-arizaGlobalSouthLeadership2023]. Return research results to the communities in which you work [@kainerGraduateEducationFramework2006]. Treat the parataxonomists, field technicians, and station staff that make our work possible with the respect they deserve [@bassetConservationBiologicalMonitoring2004]. Publish in national journals [@brunaHeliconiaAcuminataReproductive2004e].
   
**_Build on public fascination with the tropics._** Public fascination with the tropics and their charismatic species [@albertTwentyMostCharismatic2018] provides unparalleled opportunities for outreach and education [@moreiraTamarProjectConservation2017]. Take advantage of global sporting events [@meloFootballBiodiversityConservation2014], teams with tropical species as mascots [@sartore-baldwinExaminingSportFans2019], movies set in the tropics [@yongReelConservationCan2011], tropical images in fashion [@kuteskoAdidasShowsChanging2014], or other connections between people's interests and tropica biodiversity. Find ways to leverage this universal appeal into support for tropical research and conservation.

**_Get in the Game._** Help make the process of publishing more fair by serving as a review or subject editor for _Biotropica_. Contribute to capacity building efforts by reviewing student seed grants proposals or serving as a judge for student presentations at the annual meeting. Join an ATBC committee or chapter and organize a webinar, workshop, hackathon, or reading group. What should the Association be doing differently? Communicate your ideas to the ATBC leadership or stand for election and push for change as a Councillor. 

**_Support and celebrate one another._** Finally, remember that the work done by tropical biologists addresses the "neglected problems that afflict most of the world's people" [@annanChallengeWorldScientists2003]. Conducting research --- regardless of the subject --- advances the socioeconomic condition of the country in which it's conducted. It is difficult, frustrating, and not without risk. Take a moment to thank, congratulate, and support each other [@nordsethFieldworkWellnessFramework2023; @rudzkiGuideDevelopingField2022] for your contributions and the effort and resilience that they required --- you're truly making the world a better place.


<!--- really proud of ourselves. One, thanks a lot, especially with the university. They just wonderful partners. And, you know, I will tell you that Harvard, although it was officially founded in 1636, they were only incorporated in 1658. So your head of Harvard. -->


\newpage

```{r kwtable, echo = FALSE,message=FALSE,warning=FALSE}

pubs_per_pub_cat <- kw %>%
  group_by(pub_cat_2) %>%
  summarise(n_pubs = n_distinct(refID)) %>%
  ungroup() %>%
  arrange(pub_cat_2, desc(n_pubs))

# Top Keywords by pub cat
rankings_pub <- kw %>%
  group_by(pub_cat_2, final) %>%
  tally() %>%
  arrange(pub_cat_2, desc(n)) %>%
  group_by(pub_cat_2) %>%
  # slice_head(n=100) %>%
  arrange(pub_cat_2, desc(n)) %>%
  left_join(pubs_per_pub_cat) %>%
  group_by(pub_cat_2) %>%
  mutate(perc_pubs_wth_kw = (n / n_pubs * 100)) %>%
  group_by(pub_cat_2) %>%
  arrange(pub_cat_2, desc(n)) %>%
  mutate(rank_perc = rank(desc(n),  ties.method = c("random"))) %>%
  # mutate(rank_perc = min_rank(desc(n))) %>%
  # arrange(rank_perc,jrnl_cat,desc(pub_cat_2))
  arrange(desc(pub_cat_2),rank_perc) %>% 
  mutate(system = if_else((final %in% system$value == TRUE), "Y", "N")) %>%
  mutate(system = as.factor(system)) %>% 
  filter(rank_perc<=5000)


in_both <- rankings_pub %>%
  filter(rank_perc<=cutoff) %>% 
  group_by(final) %>%
  summarise(n2 = n()) %>%
  filter(n2 > 1) %>%
  mutate(both = TRUE) %>% 
  mutate(original=final)





plot_kw <- full_join(rankings_pub, in_both, by = "final") %>% 
  select(-n2) %>% 
  replace_na(list(
    "both" = FALSE
    )) %>% 
  rename(cat=pub_cat_2) 
  

trop_kw <- plot_kw %>%
  filter(cat == "tropical") %>%
  select(final, cat, rank_perc, system) %>%
  # mutate(final=paste(rank_perc,final,sep=": "))
  mutate(original=final) %>% 
  mutate(final = paste(final," (", rank_perc, ")",  sep = ""))
  # mutate(final = paste("(", rank_perc, ") ", final, sep = ""))

nontrop_kw <- plot_kw %>%
  filter(cat == "general") %>%
  select(final, cat, rank_perc, system) %>%
  mutate(original=final) %>% 
  mutate(final = paste(final," (", rank_perc, ")",  sep = ""))
  # mutate(final = paste(final, " (", rank_perc, ")", sep = ""))

nontrop_kw_2 <- plot_kw %>%
  filter(cat == "general") %>%
  select(final, cat, rank_perc, system) %>%
  mutate(final = paste("(", rank_perc, ") ", final, sep = ""))





# three keyword list --- trop, nontrop, overlap 


# in_both <- in_both %>% mutate(original=final)


trop<-trop_kw %>% filter(rank_perc<=cutoff) %>% anti_join(in_both,by="original") %>% select(cat,final,system_tropical=system)
not<-nontrop_kw %>% filter(rank_perc<=cutoff) %>% anti_join(in_both,by="original")%>% select(cat,final,system_general=system) 

both<-inner_join(trop_kw,in_both,by="original") %>% 
  inner_join(nontrop_kw,in_both,by="original") %>% 
  mutate(final.x=paste(original," (", rank_perc.x,", ",rank_perc.y,")",sep="")) %>% 
  # mutate(final.x=paste(final.x, " (",rank_perc.y,")",sep="")) %>% 
  rename(rank_perc_trop=rank_perc.x,
         rank_perc_non=rank_perc.y,
         system=system.x
         ) %>% 
  select(-system.y,-final.y) %>% 
  filter(is.na(original)==FALSE) %>% 
  filter(rank_perc_trop<=cutoff) %>% 
  filter(rank_perc_non<=cutoff) %>% 
  select(final=final.x,system_both=system) %>% mutate(cat="both")

# unique_trop_kw
# unique_nontrop_kw
# in_both_kw



df_table1<-bind_rows(trop,not,both) %>% 
  mutate(index=row_number()) %>%  
  pivot_wider(values_from = "final",names_from = "cat") %>%
  group_by(index) %>%  # this and the next two lines are to move numbers up in the place of the empty NA
  mutate_all(funs(.[order(is.na(.))])) %>% 
  filter_at(vars(tropical:general), any_vars(!is.na(.))) %>% 
  # select(-index) %>% 
  remove_empty("rows") %>%
    mutate(tropical = cell_spec(tropical, bold=ifelse(system_tropical == "Y", TRUE, FALSE))) %>%
  mutate(general = cell_spec(general, bold=ifelse(system_general == "Y", TRUE, FALSE))) %>%
  mutate(both = cell_spec(both, bold=ifelse(((is.na(system_both)==FALSE) & (system_both == "Y")), TRUE, FALSE))) %>%
  mutate(both=gsub("NA", " ", both)) %>%
  # mutate(both=ifelse(is.na(system_both)==TRUE, NA, both)) %>%
  ungroup() %>% 
  select(-index,-system_both,-system_tropical,-system_general) 


df_table1 %>% 
  kbl(
    caption = "Top keywords in tropical articles, non-tropical articles, and keywords that the categories havein common. Keywords in bold refer to species, geographic locations, or systems.",
      col.names = c("(rank)",
                   "(rank)",
                   "(rank in Tropical, Nontropical)"
                   ),
      escape = FALSE,
      align = "ccc", 
     # "latex", 
       booktabs = T, 
     linesep = "", # removes the blank line after every 5 lines 
     row.names = FALSE) %>%  
 kable_styling( 
   bootstrap_options = c("hover"), 
   full_width = F, 
   latex_options="scale_down", 
   font_size = 10, 
   position = "center" 
 ) %>%
    add_header_above(c("Top Keywords --- Tropical" = 1, 
                     "Top Keywords --- Nontropical" = 1,
                     "Top Keywords --- Shared" = 1), 
                   line=FALSE)  
```

\newpage


```{r kwtableNosystem, echo = FALSE,message=FALSE,warning=FALSE}

pubs_per_pub_cat <- kw %>%
  group_by(pub_cat_2) %>%
  summarise(n_pubs = n_distinct(refID)) %>%
  ungroup() %>%
  arrange(pub_cat_2, desc(n_pubs))

# Top Keywords by pub cat
rankings_pub <- kw %>%
  mutate(system = if_else((final %in% system$value == TRUE), "Y", "N")) %>%
  mutate(system = as.factor(system)) %>% 
  filter(system=="N") %>% 
  group_by(pub_cat_2, final) %>%
  tally() %>%
  arrange(pub_cat_2, desc(n)) %>%
  group_by(pub_cat_2) %>%
  # slice_head(n=100) %>%
  arrange(pub_cat_2, desc(n)) %>%
  left_join(pubs_per_pub_cat) %>%
  group_by(pub_cat_2) %>%
  mutate(perc_pubs_wth_kw = (n / n_pubs * 100)) %>%
  group_by(pub_cat_2) %>%
  arrange(pub_cat_2, desc(n)) %>%
  mutate(rank_perc = rank(desc(n),  ties.method = c("random"))) %>%
  # mutate(rank_perc = min_rank(desc(n))) %>%
  # arrange(rank_perc,jrnl_cat,desc(pub_cat_2))
  arrange(desc(pub_cat_2),rank_perc) %>% 
  filter(rank_perc<=5000)



in_both <- rankings_pub %>%
  filter(rank_perc<=cutoff) %>% 
  group_by(final) %>%
  summarise(n2 = n()) %>%
  filter(n2 > 1) %>%
  mutate(both = TRUE) %>% 
  mutate(original=final)

plot_kw <- full_join(rankings_pub, in_both, by = "final") %>% 
  select(-n2) %>% 
  replace_na(list(
    "both" = FALSE
    )) %>% 
  rename(cat=pub_cat_2) 

trop_kw <- plot_kw %>%
  filter(cat == "tropical") %>%
  select(final, cat, rank_perc) 

nontrop_kw <- plot_kw %>%
  filter(cat == "general") %>%
  select(final, cat, rank_perc) 



tropical<-trop_kw %>% filter(rank_perc<=cutoff) %>% anti_join(in_both,by="final") %>% rename(rank_trop=rank_perc) %>% 
  mutate(system_tropical = if_else((final %in% system$value == TRUE), "Y", "N")) 
not<-nontrop_kw %>% filter(rank_perc<=cutoff) %>% anti_join(in_both,by="final") %>% rename(rank_not=rank_perc) %>% 
  mutate(system_general = if_else((final %in% system$value == TRUE), "Y", "N")) 

both<- inner_join(trop_kw,in_both,by="final") %>% 
  inner_join(nontrop_kw,in_both,by="final") %>% 
  rename(rank_perc_trop=rank_perc.x,
         rank_perc_non=rank_perc.y
         ) %>% 
  select(-cat.y,-n2,-both,-original,-cat.y,-cat.x) %>% 
  filter(is.na(final)==FALSE) %>% 
  filter(rank_perc_trop<=cutoff) %>% 
  filter(rank_perc_non<=cutoff) %>% 
  mutate(cat="both") %>% 
mutate(system_both = if_else((final %in% system$value == TRUE), "Y", "N")) 


df_table2<-bind_rows(tropical,not,both) %>% 
  mutate(index=row_number()) %>%  
  pivot_wider(values_from = "final",names_from = "cat") %>%
  group_by(index) %>%  # this and the next two lines are to move numbers up in the place of the empty NA
  mutate_all(funs(.[order(is.na(.))])) %>% 
  filter_at(vars(tropical:general), any_vars(!is.na(.))) %>% 
  select(-index) %>% 
  remove_empty("rows") %>%
  mutate(across(c(tropical,general,both),  
               ~ case_when(is.na(.)==TRUE~ "",  
                           is.na(.)==FALSE ~.))) %>% 
  relocate(rank_trop,.before=tropical) %>% 
  relocate(rank_not,.before =general) %>% 
  relocate(rank_perc_trop,.before=both) %>% 
  relocate(rank_perc_non,.before=both) %>% 
  ungroup() %>% 
  select(-index) %>% 
  mutate(tropical=paste(tropical, " (",rank_trop,")", sep="")) %>% 
  mutate(both=paste(both, " (",rank_perc_trop,",",rank_perc_non,")", sep="")) %>%
  mutate(general=paste(general, " (",rank_trop,")", sep="")) %>% 
 mutate(both=gsub("\\(NA,NA\\)","",both)) %>% 
    mutate(tropical = cell_spec(tropical, bold=ifelse(system_tropical == "Y", TRUE, FALSE))) %>%
  mutate(general = cell_spec(general, bold=ifelse(system_general == "Y", TRUE, FALSE))) %>%
  mutate(both = cell_spec(both, bold=ifelse(((is.na(system_both)==FALSE) & (system_both == "Y")), TRUE, FALSE))) %>%
  mutate(both=gsub("NA", " ", both)) %>%
  mutate(tropical=gsub("NA", " ", tropical)) %>%
  mutate(general=gsub("NA", " ", general)) %>%
  # mutate(both=ifelse(is.na(system_both)==TRUE, NA, both)) %>%
  ungroup() %>% 
  select(tropical,general,both) 

df_table2 %>% 
  kbl(
    caption = "Top keywords from tropical and non-tropical articles that are unique to each category once system-specific keywords have been excluded, followed by the top keywords from each category that they have in common. Keywords in bold refer to species, geographic locations, or systems.",
      col.names = c("(rank)",
                   "(rank)",
                   "(rank in Tropical, Non-Tropical)"
                   ),
      escape = TRUE,
      align = "ccc", 
     # "latex", 
       booktabs = T, 
     linesep = "", # removes the blank line after every 5 lines 
     row.names = FALSE) %>%  
 kable_styling( 
   bootstrap_options = c("hover"), 
   full_width = F, 
   latex_options="scale_down", 
   font_size = 12, 
   position = "center" 
 ) %>%
    add_header_above(c("Top Keywords --- Tropical" = 1,
                     "Top Keywords --- Nontropical" = 1,
                     "Top Keywords --- Shared" = 1), 
                   line=FALSE) 

```

```{r fig-org, fig.align="center", out.width = "100%", fig.cap='(A) Alternative ways in which researchers self-organize: scholarly societies focused on (a) Conceptual Domains, (b) Systemic Domains, or (c) Methodological Domains. The Association for Tropical Biology transcends these three, as it has members that study a wide variety of systems using different conceptual approaches and tools.'}
ggdraw() + draw_image('./manuscript/figures_2/slide4.png', scale = 1)
```


\newpage

```{r fig-temp, fig.align="center", out.width = "100%", fig.cap='The logo for a proposed new scholarly society for researchers specializing on temperate ecosystems.'}
ggdraw() + draw_image("./manuscript/figures_2/slide2.png", scale = 1)
```

\newpage

```{r fig-pubs, fig.align="center", out.width = "100%", fig.cap='Alternative publication titles whose framing assumes the \'reference\' ecosystem is (A) the Temperate Zone (B) the Tropics.'}
ggdraw() + draw_image("./manuscript/figures_2/slide1.png", scale = 1)
```
\newpage

<!-- ```{=tex} -->
<!-- \newpage -->
<!-- \blandscape -->
<!-- ``` -->


<!-- ```{=tex} -->
<!-- \elandscape -->
<!-- \newpage -->
<!-- ``` -->


## ACKNOWLDGEMENTS  
I am grateful to the organizers of the 2022 Meeting of the ATBC for encouraging the Presidential Plenary on which this essay is based, to J. Powers for her outstanding editorial work, and to P. Delamônica for her unending support and insights. This essay is dedicated to the memory of Emilio Bruna Jr.


## DATA AVAILABILITY STATEMENT  
The complete data set used in this article is available in Dryad at <_DOI added upon acceptance_>. The version of the code used to review, correct, and prepare this archive (version 1.0.0) is available at Zenodo at <_DOI added upon acceptance_>. The code used to prepare this publication, including statistical summaries reported in the text, tables, and figures, is available at Zenodo at <_DOI added upon acceptance_>.

## DISCLOSURE STATEMENT  
The author confirms that there have been no involvements that might raise the question of bias in the work reported or in the conclusions, implications, or opinions stated.

\newpage


# References  

&nbsp;



::: {#refs custom-style="Bibliography"}
:::

\newpage


# SUPPLEMENTARY MATERIALS {-}


```{r child = "./manuscript/bruna_supplement.Rmd"}
```




<!-- let's start with the first one. it's that word: 'specialized'. That adjective in front of the word biology implies that we are somehow specialized, narrower, right? So we're, we're not biology, we're tropical biology. And what that really implies, I think, is one of three things. Either that, you know, things are specialized sub disciplines, because of the approach or the tools that they use, right. So, you know, you might use a particular approach or tools in a way that crosses systems and conceptual domains. And that's why you're nested within this kind of broader sphere of biology. And so, you know, there are academic societies that are structured that way, right? So as a member of the ATBC, someone who's active here, I think, in you know, societies as useful organizations focusing on particular interests to the scientific community. So here you might have mathematical biology or cell biology or experimental biology, in vitro biology, right? Those are all adjectives that tell you something about the specialization of approaches and tools even if it crosses conceptual domains.  -->

<!-- 2) Another approach might be to organize Your academic societies your organization's around conceptual domains that instead cross systems and approaches, right.  -->

<!-- And these different conceptual domains all tell you something about the way in which biology operates.  -->

<!-- And so this could be something like the Society for conservation biology, right? Or systematic biology, ethno biology or evolutionary biology, right.  -->

<!-- So you can do evolutionary biology and lots of different systems and using lots of different tools.  -->

<!-- It's the conceptual organizing focus of evolution by natural selection that gets you to be a member of that society, because you have something in common with people who have that similar conceptual focus.  -->


<!-- 3) And the third thing, of course, could be that you're specialized because you work on a particular study system.  -->

<!-- And the people working on that study system might approach it in different conceptual ways, or using different tools, but they're all interested in that system.  -->

<!-- And that could be either a taxonomic system, right? Avian biology, fish biology, Master mussels, Elysia, it could be plant biology.  -->

<!-- It could in theory, be something that's kind of geological or geographic.  -->

<!-- So there, there's a society for Island biology, there's an International Mountain society, which focuses a lot on the biology of mountain ecosystems.  -->

<!-- And it could be bio geographic, which gets a little closer to I think, what people think about when they're talking about tropical biology, right, there are a couple of national grassland societies.  -->

<!-- But there's not really much in the way of scholarly organization, scholarly societies like ours, that are focused on bio geographic regions, or biomes.  -->

<!-- Right? If you think about it, there, there was a Mediterranean biologist society, it's kind of kind of fine.  -->

<!-- There's Oh, there is an early career scholars in polar biology, but there's no you know, there's no tundra biology society, right? There are some journals that focus on these things, but, but it's not enough to bring people from around the world together into one place.  -->

<!-- Think about things.  -->



<!-- ```{r top_tw, echo = FALSE,message=FALSE,warning=FALSE,fig.cap='Main Title words.'} -->
<!-- # Titleword analysis -->

<!-- # Load keyword records  ----------------- -->

<!-- tw_all<-read_csv(here("bibliometrics","data_clean","tw_clean.csv")) %>%  -->
<!--   mutate(pub_cat=as.factor(pub_cat_2)) %>%  -->
<!--   mutate(jrnl_cat=as.factor(jrnl_cat)) %>%  -->
<!--   mutate(index = row_number()) %>%  -->
<!--   mutate(pub_cat_2=as.factor(pub_cat_2)) -->



<!-- tw_trop <-tw_all %>%  -->
<!--   drop_na(final) %>%  -->
<!--   filter(pub_cat_2 == "tropical") %>%  -->
<!--   distinct(refID,final) %>%  -->
<!--   group_by(final) %>%  -->
<!--   tally(n_distinct(refID)) %>% -->
<!--   arrange(desc(n)) %>%  -->
<!--   mutate(perc=n/sum(n)*100) %>%  -->
<!--   mutate(cat="Tropical") %>%  -->
<!--   mutate(rank=row_number()) -->



<!-- tw_non<-tw_all %>%  -->
<!--   drop_na(final) %>%  -->
<!--   filter(pub_cat_2 == "general") %>%  -->
<!--   distinct(refID,final) %>%  -->
<!--   group_by(final) %>%  -->
<!--   tally(n_distinct(refID)) %>% -->
<!--   arrange(desc(n)) %>%  -->
<!--   mutate(perc=n/sum(n)*100) %>%  -->
<!--   mutate(cat="Nontropical") %>%  -->
<!--   mutate(rank=row_number()) -->

<!-- single_tw_long<-bind_rows(tw_trop,tw_non) %>% filter(rank<51)   -->

<!-- single_tw_both<-single_tw_long %>%  -->
<!-- group_by(cat) %>%  -->
<!--   arrange(rank) %>%  -->
<!--   # slice(1:50) %>%  -->
<!-- group_by(final,.drop=FALSE) %>%  -->
<!--   tally() %>%  -->
<!--   mutate(cat2=if_else(n>1,"Both",NA)) %>%  -->
<!--   drop_na(cat2) %>%  -->
<!--   select(-n) -->


<!-- single_tw_wide<-single_tw_long %>%  -->
<!--   left_join(single_tw_both,by="final") %>%  -->
<!--   filter(rank<51) %>%  -->
<!--   mutate(cat2=if_else(is.na(cat2),cat,cat2)) %>%  -->
<!--   pivot_wider(names_from = cat2, -->
<!--               values_from = final)  -->

<!-- tw_both<-single_tw_wide %>% ungroup() %>% select(Both) %>% arrange(Both) %>% unique() -->
<!-- tw_tropical<-single_tw_wide %>% ungroup() %>% select(tropical) %>% arrange(tropical) -->
<!-- tw_nontropical<-single_tw_wide %>% ungroup() %>% select(nontropical) %>% arrange(nontropical) -->

<!-- counter<-max(nrow(tw_both),nrow(tw_tropical),nrow(tw_nontropical)) -->
<!-- add_tw<-as.data.frame(rep(NA,(counter-nrow(tw_both)))) -->
<!-- names(add_tw)<-"Both" -->
<!-- tw_both<-bind_rows(tw_both,add_tw) -->


<!-- table_tw<-bind_cols(tw_both,tw_tropical,tw_nontropical) %>% -->
<!--   remove_empty("rows") %>%  -->
<!--   mutate(across(c(Both,tropical,nontropical),  -->
<!--                 ~ case_when(is.na(.)==TRUE~ "",  -->
<!--                             is.na(.)==FALSE ~.))) -->
<!-- kbl(table_tw, -->
<!--       # digits = 2, -->
<!--       align = "ccc", -->
<!--       # "latex", -->
<!--       row.names = FALSE, -->
<!--       escape = TRUE, -->
<!--       booktabs = T, -->
<!--       linesep = "" # removes the blank line after every 5 lines -->
<!-- ) %>% -->
<!--   kable_styling( -->
<!--     bootstrap_options = c("hover"), -->
<!--     full_width = F, -->
<!--     latex_options="scale_down", -->
<!--     font_size = 12, -->
<!--     position = "center" -->
<!--   ) -->

<!-- ``` -->

<!-- <!-- --- It is cross-conceptual, cross-tool, and cross-system --- it simply doesn't fit neatly into any of these specialization categories along which scholars typically self-organize.  --> 

<!-- \newpage -->

<!-- ```{r bigrams, echo = FALSE,message=FALSE,warning=FALSE} -->
<!-- # BIGRAMS -->

<!-- extract_ngram_data <- function(tw) { -->
<!--   ngram_data<-tw %>% -->
<!--     select(refID,PY,SO,pub_cat_2,jrnl_cat,final) %>% -->
<!--     arrange(refID,PY,SO) %>% -->
<!--     group_by(refID,PY,SO) %>% mutate(word=row_number()) %>% -->
<!--     relocate(word,.before=final) %>% -->
<!--     mutate(place="place") %>% -->
<!--     relocate(place,.before=word) -->
<!--   # %>% -->
<!--   #   replace_na(list(final="-")) -->
<!--   ngram_data<-ngram_data %>% replace_na(list(final= "deleteme")) %>% -->
<!--     pivot_wider(names_from = c(place,word), -->
<!--                 values_from = final, -->
<!--                 values_fn = list, values_fill = list("deleteme") -->
<!--     ) %>% -->
<!--     ungroup() -->

<!--   last_col<-ngram_data %>% select(last_col()) -->
<!--   last_col<-last(names(ngram_data)) -->
<!--   ngram_data<- ngram_data %>% -->
<!--     unite("tw", place_1:last_col, na.rm = FALSE, remove = TRUE, sep= " ") %>% -->
<!--     ungroup() -->
<!--   return(ngram_data) -->
<!-- } -->

<!-- ngram_data<-extract_ngram_data(tw_all) -->


<!-- generate_bigrams <- function(ngram_data) { -->

<!--   n_titles<-ngram_data %>% summarize(n=n_distinct(refID)) -->

<!--   tw_bigrams <- ngram_data %>% -->
<!--     select(tw,refID) %>% -->
<!--     # slice(1:100) %>% -->
<!--     unnest_tokens(bigram, tw, token = "ngrams", n = 2) %>% -->
<!--     distinct(refID,bigram) -->

<!--   # %>% -->
<!--   #   count(refID,bigram, sort = TRUE) -->
<!--   bigrams_separated <- tw_bigrams %>% -->
<!--     separate(bigram, c("word1", "word2"), sep = " ") -->
<!--   bigrams_filtered <- bigrams_separated  %>% -->
<!--     filter(!word1 %in% stop_words$word) %>% -->
<!--     filter(!word2 %in% stop_words$word) %>% -->
<!--     # arrange(desc(n)) %>% -->
<!--     filter(str_detect("deleteme",word1,negate=TRUE)) %>% -->
<!--     filter(str_detect("deleteme",word2,negate=TRUE)) -->
<!--   # slice(1:1000) -->


<!--   bigrams_filtered<-bigrams_filtered %>% -->
<!--     # filter(nchar(word1)<4) %>% -->
<!--     mutate(word1_first=substring(word1, 1, 1)) %>% -->
<!--     mutate(word2_first=substring(word2, 1, 1)) %>% -->
<!--     mutate(number=case_when( -->
<!--       (str_detect(word1_first,".*[0-9].*")) == TRUE ~ "number", -->
<!--       (str_detect(word2_first,".*[0-9].*")) == TRUE ~ "number", -->
<!--       TRUE ~ "keep")) %>% -->
<!--     filter(number=="keep") %>% -->
<!--     select(-number,-word1_first,-word2_first)  %>% -->
<!--     group_by(word1,word2) %>% -->
<!--     summarize(n=n()) %>% -->
<!--     arrange(desc(n)) %>% -->
<!--     mutate(perc=n/n_titles$n*100) -->
<!--   return(bigrams_filtered) -->
<!-- } -->



<!-- # bigrams<-generate_bigrams(ngram_data) -->


<!-- ngram_data_gen<-ngram_data %>% filter(pub_cat_2=="general") -->
<!-- ngram_data_trop<-ngram_data %>% filter(pub_cat_2=="tropical") -->


<!-- NonTrop_bigrams<-generate_bigrams(ngram_data_gen) %>% -->
<!--   mutate(cat="nontropical") -->


<!-- Trop_bigrams<-generate_bigrams(ngram_data_trop) %>% -->
<!--   mutate(cat="tropical") -->




<!-- bigrams_long<-bind_rows(NonTrop_bigrams,Trop_bigrams) %>% -->
<!--   unite("bigram", word1:word2,sep= " ", remove=TRUE) %>% -->
<!--   group_by(cat) %>% -->
<!--   arrange(desc(n)) %>% -->
<!--   mutate(rank=row_number()) -->


<!-- bigrams_both<-bigrams_long %>% -->
<!--   group_by(cat) %>% -->
<!--   arrange(rank) %>% -->
<!--   slice(1:50) %>% -->
<!--   group_by(bigram,.drop=FALSE) %>% -->
<!--   tally() %>% -->
<!--   mutate(cat2=if_else(n>1,"Both",NA)) %>% -->
<!--   drop_na(cat2) %>% -->
<!--   select(-n) -->

<!-- bigrams_wide<-bigrams_long %>% -->
<!--   left_join(bigrams_both,by="bigram") %>% -->
<!--   filter(rank<51) %>% -->
<!--   mutate(cat2=if_else(is.na(cat2),cat,cat2)) %>% -->
<!--  pivot_wider(names_from = cat2, -->
<!--                values_from = bigram) -->



<!-- bigrams_both<-bigrams_wide %>% ungroup() %>% select(Both) %>% arrange(Both)%>% unique() -->
<!-- bigrams_tropical<-bigrams_wide %>% ungroup() %>% select(tropical) %>% arrange(tropical)%>% unique() -->
<!-- bigrams_nontropical<-bigrams_wide %>% ungroup() %>% select(nontropical) %>% arrange(nontropical)%>% unique() -->


<!-- counter<-max(nrow(bigrams_both),nrow(bigrams_tropical),nrow(bigrams_nontropical)) -->
<!-- add_bigrams<-as.data.frame(rep(NA,(counter-nrow(bigrams_both)))) -->
<!-- names(add_bigrams)<-"Both" -->
<!-- bigrams_both<-bind_rows(bigrams_both,add_bigrams) -->

<!-- table_bigrams<-bind_cols(bigrams_both,bigrams_tropical,bigrams_nontropical) -->

<!-- table_bigrams<-table_bigrams %>% -->
<!--   remove_empty("rows") %>% -->
<!--   mutate(across(c(Both,tropical,nontropical), -->
<!--                 ~ case_when(is.na(.)==TRUE~ "", -->
<!--                             is.na(.)==FALSE ~.))) -->



<!--   kbl(table_bigrams, -->
<!--       digits = 2, -->
<!--       align = "ccc", -->
<!--       format = "latex", -->
<!--       row.names = FALSE, -->
<!--       escape = TRUE, -->
<!--       booktabs = T, -->
<!--       # caption = "Text Caption", -->
<!--       linesep = "" # removes the blank line after every 5 lines -->
<!-- ) %>% -->
<!--   kable_styling( -->
<!--     bootstrap_options = c("hover"), -->
<!--     full_width = F, -->
<!--     latex_options="scale_down", -->
<!--     font_size = 12, -->
<!--     position = "center" -->
<!--   ) -->

<!-- ``` -->


<!-- The tropics were either paradise right, Sir Walter Raleigh said that if there's anywhere on Earth, that's as close as there is to the Garden of Eden, it's in the tropics, right? And you see this in both the written word you might see it in artistic works like this painting by Alberta couture was a Dutch painter in Brazil in the late 1600s.  -->
<!-- The alternative, of course, is that the tropics were hell on earth, right? There were health escapes, they're full of disease and dangerous people, they, you know, they were the source of madness.  -->
<!-- You know, recent politicians, at least in the United States, where I live refer to tropical countries in really derogatory ways, in part because this is one of the narratives that they've been hearing for centuries about the tropics, right? Not just about the, the conditions there, but the people that live in the tropics as well.  -->
<!-- I mean, Marco Polo wrote some really beautiful things about some tropical people And then wrote some really awful things about others.  -->
<!-- And then the third thing that you see is that the tropics, in part, because of these other two things, are our destinations for self discovery, as well as discovery in quotes right of a lot of these natural resources, and about proving oneself.  -->
<!-- That's why people go to the tropics, because either they have this insatiable drive, they can't understand like Von Humboldt, who was just driven and just had to go all the time.  -->
<!-- Or you had daddy issues like Darwin did.  -->
<!-- And the way you proved yourself was by going to the tropics, or you were Teddy Roosevelt, who was frustrated because his political party didn't nominate him to run for president.  -->
<!-- So the way he dealt with that, and got that out of his system, was calling up then Colonel now later Machelle horns on and deciding to explore this tributary in the Amazon that he thought that would be just a really cool way to get over his massive disappointment and not having leadership of the country handed to him.  -->
<!-- And so what you get is the the tropics visited by early Europeans, they come back with narratives about these topics which are consumed by the public and transformed by the public, then share it again in new narratives.  -->
<!-- And ultimately, what you end up is then multiple different versions of what the tropics are.  -->
<!-- And this happened repeatedly and repeatedly and repeatedly.  -->
<!-- And it's happened for centuries and centuries and centuries, to the point where you see these tropes repeated in high art and low art in every aspect of our lives.  -->
<!-- You can trace through these different tropes back to the original writings of people like Sir Walter Raleigh are really Franciscans working through the Americas.  -->
<!-- I mean, if you were to go through high art, it would be Caucasian or Richard Kipling.  -->
<!-- You know, and Fitzcarraldo.  -->
<!-- That's all about proving yourself right, if you want to do instead you know, Tarzan, Eat, Pray, Love.  
<!-- You know, Anaconda.  -->
<!-- This is for me talk about mixed metaphors.  -->
<!-- This is Dolce and Gabbana is 2020 collection, and it's women wild in the jungle, like modern nymphs.  -->
<!-- So we're taking Greek mythology and mixing it with like, generic jungle stuff with a nice smattering of colonialism in there.  -->
<!-- It's, it's just wild, right, and this is this generic interpretation of what the tropics are.  -->
<!-- In fact, the historian David Arnold, who said that, calling a part of the globe, the tropics became a Western way of defining something environmentally and culturally distinct from Europe.  -->
<!-- But also perceiving a high degree of common identity perceiving a high degree of common identity between the constituent regions of the tropical world.  -->
<!-- In other words, it's a way of setting the tropics apart as other while also smoothing over any differences, right? It makes it easier to separate something as distinct when you ignore all the differences that there are within that region that you're considering different from yourself.  -->
<!-- And so you end up over the centuries of this work, reinforcing and manipulating and twisting ideas about what the tropics are, with this kind of platonic ideal of what a tropical field site is.  -->
<!-- And the fact is that this slide has been up for 30 seconds that everybody looks at and goes yeah, this looks like they're trying to figure out where exactly is this place because it looks like an awesome place to go and do some botanizing I think maybe there's one person in the room who realizes that this isn't actually a tropical field site.  -->
<!-- This is Pandora's world of Avatar and Disney World.  -->
<!-- And the reason it looks like so many of the places we work is because that's what Pandora is right? It avatar is really just, frankly, the last rainforest in space.  -->
<!-- This is what they think exotic distant destinations look like.  -->
<!-- They look like the tropics, they look like the places we work, because that's what explorers do, they go to jungles.  -->
<!-- And so the tropics is other and your need became this kind of paradigm for the way we approach the world.  -->
<!-- And scientifically, then that was translated into the biology of the tropics is unique.  -->
<!-- And the same cultural reinforcements about what the tropics were, were absorbed by academics in Europe, and in the United States, who had these ideas in mind when they were formalizing the field of ecology and the field of evolutionary biology, which sets us today, if you have not read this book by Megan rappi, American tropics, it's just a great great reach as a historian at UT Austin, wrote about the Caribbean roots of biodiversity science and how researchers in the United States who were interested in studying biodiversity and understanding why, you know, the origins of biodiversity, then look to the tropics, and decided to establish places in the tropics where they could go do their research and come back and it's worth a read.  -->
<!-- So I'll just use one pull quote from it, which I think is really great, which is that he writes our field is a colonial science.  -->
<!-- Visiting researchers from the United States encountered Panamanians as cooks, or mechanics, writing about what became the Smithsonian, about BCI.  -->
<!-- As cooks, or mechanics, but rarely, as fellow academics, I will tell you this, this is not the case in all of the field stations.  -->
<!-- And this is one of the things that's really interesting is the different ways in which field stations in the tropics operated in different ways in relationship to both local scientists and the scientists that were coming from abroad.  -->
<!-- And so you have this perception of the tropics as different and exotic, and novel and away, right, remote, they were distant, coupled with going and leaving and not interacting with anybody actually, in the tropics when you were there.  -->
<!-- And things like the broader geographical notions of what the world was operating under, you know, this is a typical Mercator projection.  -->
<!-- I've seen several of these in presentations here already in the last couple of days.  -->
<!-- And inside of that is the actual area of countries that are represented there, right.  -->
<!-- And this has come, you know, common among geographers will tell you that the way we see countries in the typical Mercator projection is that a lot of us grew up with reinforced notions of, you know, what countries are big and which ones are small.  -->
<!-- And that translates in many ways, indirectly coupled with his imagery about both the places and the people who live there.  -->
<!-- And so what you ended up constructing was this notion that the biology of the tropics is unique.  -->
<!-- And that means that the tropics are apart, and they can inform our understanding of biology, I've got a stack of articles over there in my backpack from the 40s 50s and 60s, mostly with variance around the title of what the tropics can teach us about biology, right? The tropics are part, there's a biological Foundation, which is really a temperate Foundation.  -->
<!-- And tropical biology is helping to fine tune our understanding of biological systems.  -->
<!-- This is what it means for tropical biology to be specialized.  -->
<!-- There's biology, and then there's tropical biology, which can tell us a little bit about how most biological systems operate.  -->
<!-- And of course, this is, you know, absurd on its face.  -->
<!-- Within the tropics, explicitly defined, right? You have majority of biodiversity, you have roughly 40% of the terrestrial land area, it's not a specialization, it's nearly half.  -->
<!-- The bottom left, you'll see human population by latitude, currently, within the tropics, you have about 43% of the human population just a little more if you're willing to go to about 25 degrees latitude, but by 2025, it's predicted that exactly half the people in the world will be in the tropics.  -->
<!-- And there on the bottom right, is also the emergence of global mega cities of over 10 million people.  -->
<!-- A lot of which will be emerging in the tropics as well.  -->
<!-- So it's not that the tropics are other and smaller and narrower and unique, that tropics are actually the foundation right? This is the baseline.  -->
<!-- This is where most of the biology is happening.  -->
<!-- It's where most of the action is it's where at least half the people are.  -->   




<!-- Despite comprising the vast majority of the planet's terrestrial biodiversity [@gastonGlobalPatternsBiodiversity2000], ~40% of its terrestrial surface area, and half the human population [@hoornwegPopulationPredictionsWorld2017],  -->
<!--  but as far as I knew there were no "specialized journals focusing on _temperate_ biology."  -->


 <!-- ^[is is also evident that much of our current teaching in ecology, as well as in other branches of biology, would be set in a truer perspective if more consideration were given to tropical vegetation and the conditions for plant growth in the tropics" [@richardsNeedDevelopmentTropical1946];
  
  "The science of ecology developed first in central Europe, Scandinavia and Britain and very slightly later in the United States. The ideas and concepts with which it started were therefore inevitably based on the conditions in a temperate climate where the land has been long and intensively occupied by man." [@richardsWhatTropicsCan1963]] -->

  <!-- ^["Now at first sight the tropics are not a promising field for the ecologist. Tropical vegetation is reputed to be monotonous. It certainly contains far too many species for comfort and most of them are very difficult to identify"] -->

<!-- "I believe, nevertheless, that ecology which is not based as much on a knowledge of tropical as well as of temperate vegetation in relation to its environment is bound to be in some respects misleading as well as incomplete." Richards -->

<!-- "The science of ecology developed first in central Europe, Scandinavia and Britain and very slightly later in the United States. The ideas and concepts with which it started were therefore inevitably based on the conditions in a temperate climate where the land has been long and intensively occupied by man." -->

<!-- "In what way will a more intensive study of ecology in the tropics be likely to alter our present ecological ideas? In other words what can the tropics contribute to ecology?" -->

<!-- . I only want to say that I think the British Ecological Society can play a part by stimulating and keeping alive an interest in tropical ecology, especially by providing a forum where those interested in the subject can meet, discuss and read papers, and also by publishing their work in its journals.  -->

<!-- "Our two existing journals, the Journal of Ecology and the Journal of Animal Ecology have published many papers on tropical ecology in the past and I hope they will continue to do so in the future. This has meant, and will probably continue to mean for some time, publishing a fair number of papers which are mainly descriptive and therefore inevitably rather long. Members of the Society with different interests may perhaps regret this and wish that the precious space could be available for papers of a different type. Speaking as an editor of the Journal of Ecology I would, however, remind them that tropical ecology is likely to follow the same course of development as ecology in general and eventually to become to a large extent experimental. -->


<!-- 1. It's also why in In Brazil or India or Equador, students take courses in 'Biology', without any geographic modifier.    -->

<!-- Now, if you've heard this before, and I am sure some people have, it's because you probably maybe read this paper from an address to the Panama conference on tropical biology in 1966, by Ripley, who wrote we in the United States are natively a temperate zone oriented people, I'll save you the trouble of reading it all, which is, as a result, in the case of biology, a major part of the accumulated biological, biological knowledge is concerned with a rather minor part of the world fun and flora because of the chance development of biology in the temperate zones.  -->

