---
title             : "Is there really such a thing as _Tropical_ Biology?"
shorttitle        : "Draft for _Biotropica_"
# LRH and RRH: YAZ and PEIGH
author: 
  - name          : "Emilio M. Bruna"
    affiliation   : "1,2,3"
#    address       : "Department of Wildlife Ecology and Conservation, University of Florida, PO Box 110430, Gainesville, FL 32611-0430, USA"
    email         : "embruna@ufl.edu"
    # role:
    #   - Methodology
    #   - Data curation
    #   - Investigation
    #   - Funding acquisition
    #   - Conceptualization
    #   - Formal analysis
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft

affiliation:
  - id            : "1"
    institution   : "Department of Wildlife Ecology and Conservation, University of Florida, PO Box 110430, Gainesville, FL 32611-0430, USA"
  - id            : "2"
    institution   : "Center for Latin American Studies, University of Florida, PO Box 115530, Gainesville, FL 32611-5530, USA"

authornote: |
  Received:______; Revised:______; Accepted:______.  

  
# 
# abstract: |
#   Abstract of the paper.
  
  
  
keywords          : "Up,to,eight,keywords"
wordcount         : "X"

bibliography      : "ATBC_2022_Plenary.bib"

floatsintext      : no
linenumbers       : yes
draft             : no
mask              : no

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man, donotrepeattitle" # suppresses title on 1st page of MS
output            : papaja::apa6_pdf
mainfont: Times New Roman
fontsize: 12pt
csl: "biotropica.csl"
fig_caption: yes
keep_tex: yes
header-includes:
  - \usepackage{float} #to keep figure in the location placed instead of end
  - \floatplacement{figure}{H}
  - \usepackage{booktabs}
  - \usepackage{setspace} # line spacing
  - \raggedbottom
 # - \usepackage{endfloat} #[nomarkers] excludes the {insert figure x around here] from main text. The others exclude the list of tables and figures. https://cs.brown.edu/about/system/managed/latex/doc/endfloat.pdf
  - \usepackage{tabu}
  - \usepackage{makecell}
  - \usepackage{pdflscape}
  - \usepackage{longtable}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \setlength\parindent{22pt}
---

```{r GlobalOptions, include=FALSE}
options(knitr.duplicate.label = 'allow')
knitr::opts_chunk$set(fig.pos = "H", out.extra = "")
# knitr::opts_chunk$set(fig.pos = 'h')
```

```{r setup, include = FALSE}
library("papaja")
knitr::opts_chunk$set(echo = FALSE,message=FALSE,warning=FALSE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(knitr)
library(cowplot)
# library(egg)
library(magick)
library(citr)
# library(devtools)
# devtools::install_github("crsh/papaja")
```
\onehalfspacing
\singlespacing


> "There are few things more presumptuous than a US scientist holding forth on the future of tropical ecology" [@janzenWhitherTropicalEcology1972].

## 1. INTRODUCTION

1. Motivation: In 19XX I received a decision on a manuscript that included justification I suspect many of us have seen: 

>>”The scope of your paper makes it more appropriate for a specialized journal focusing on tropical systems"

1. This has always trouybled me, because there is an implicit (or explicit) emphasis in training students and professional advancement that broad, general conclusions should be our scientific goal. The implication of this decision is that those of us that call ourselves tropical biologists are making a less general (=less important) contribution. 

1. In recent years we have seen the re-emergence of what is actually an old conversation - the extent to which not tropical biologists, but biologists from tropical countries are excluded from the scientific process. 

1. Here I reconsider the notion that Tropical Biology is a specialized discipline of the biological sciences by considering two distinct but related  datasets - the way in which biologists self-organize into specialized groups (i.e., subdisciplines) and (2) the topics of their research and how the way in which they conceptualize their contributions to the scientific literature.   

1. I wish to emphasize that this is by no means intended to be a comprehensive historical overview of the field. Nor am I the first to have wrestled with questions about the breadth, novelty, and status of tropical biology [@janzenFutureTropicalEcology; @robinson1978tropical; @zukTemperateAssumptionsHow2016].

Instead, my goal is to stimulate discussion about the fundamental yet generally ignored question that serves as the foundation on which our association is built: Is there really such a thing as _"Tropical"_ Biology?

## 1. Why the answer might be *'No'*

<!-- 1. The adjective "Tropical" in our Association's name implies specialization.  -->
1. There are different way in which  
1. This specialization could be one of (specialization of approach and tools, conceptual domain, or study system). Figure 1.

1. 'Tropical' transcends all of these. 

1. Moreover, the tropics is transcendent: tropical species don't stop at the 23rd parallel, the adjective is rarely used in the tropics themselves, and although "tropics" has a very specific definition, biologists rarely use it...in fact, they don;t have a consistent definition. 

1. The fact is that "the tropics" as a distinct and unique entity is a historical artefact whose end result was considering the tropics as (culturally, scientifically, biologically) 'other' and 'unique'.  

<!-- let's start with the first one. it's that word: 'specialized'. That adjective in front of the word biology implies that we are somehow specialized, narrower, right? So we're, we're not biology, we're tropical biology. And what that really implies, I think, is one of three things. Either that, you know, things are specialized sub disciplines, because of the approach or the tools that they use, right. So, you know, you might use a particular approach or tools in a way that crosses systems and conceptual domains. And that's why you're nested within this kind of broader sphere of biology. And so, you know, there are academic societies that are structured that way, right? So as a member of the ATBC, someone who's active here, I think, in you know, societies as useful organizations focusing on particular interests to the scientific community. So here you might have mathematical biology or cell biology or experimental biology, in vitro biology, right? Those are all adjectives that tell you something about the specialization of approaches and tools even if it crosses conceptual domains.  -->

<!-- 2) Another approach might be to organize Your academic societies your organization's around conceptual domains that instead cross systems and approaches, right.  -->

<!-- And these different conceptual domains all tell you something about the way in which biology operates.  -->

<!-- And so this could be something like the Society for conservation biology, right? Or systematic biology, ethno biology or evolutionary biology, right.  -->

<!-- So you can do evolutionary biology and lots of different systems and using lots of different tools.  -->

<!-- It's the conceptual organizing focus of evolution by natural selection that gets you to be a member of that society, because you have something in common with people who have that similar conceptual focus.  -->


<!-- 3) And the third thing, of course, could be that you're specialized because you work on a particular study system.  -->

<!-- And the people working on that study system might approach it in different conceptual ways, or using different tools, but they're all interested in that system.  -->

<!-- And that could be either a taxonomic system, right? Avian biology, fish biology, Master mussels, Elysia, it could be plant biology.  -->

<!-- It could in theory, be something that's kind of geological or geographic.  -->

<!-- So there, there's a society for Island biology, there's an International Mountain society, which focuses a lot on the biology of mountain ecosystems.  -->

<!-- And it could be bio geographic, which gets a little closer to I think, what people think about when they're talking about tropical biology, right, there are a couple of national grassland societies.  -->

<!-- But there's not really much in the way of scholarly organization, scholarly societies like ours, that are focused on bio geographic regions, or biomes.  -->

<!-- Right? If you think about it, there, there was a Mediterranean biologist society, it's kind of kind of fine.  -->

<!-- There's Oh, there is an early career scholars in polar biology, but there's no you know, there's no tundra biology society, right? There are some journals that focus on these things, but, but it's not enough to bring people from around the world together into one place.  -->

<!-- Think about things.  -->

Tropical biology defies all of these specialization guidelines.
It is cross-conceptual, cross-tool, and cross-system - it simply doesn't fit neatly into any of these specialization categories along which scholars typically self-organize. 

But perhaps the best evidence that there really isn't such a thing as Tropical Biology is that the term is primarily used _outdside_ of the tropics. It is rare for colleges in Brazil or India or Peru to offer a course in "Tropical Biology" or "Tropical Ecology" - they simply call it "Ecology".

The tropics also defy biological definition - the distributions of "tropical" species don't end at the 23rd parallels. 

Finally, even tropical biologists can't agree on what the tropics are - Feeley and Stroud surveyed the literature and found that biologists working in the tropics defined the region at least eight different ways [@feeleyWhereEarthAre2018]. 

The reason for this divergence is that the tropics exist as an astronomical artefact - they are the points on earth that are exposed to directly overhead solar radiation for at least one day. 

Their existence in the colloquial sense - as a distinct region - is actually a historical artifact that traces its origins back to Marco Polo. He was not the first european to visit the tropics in search of spices like cinnamon and nutmeg, but he was the first person whose vivid descriptions about the things he saw mesmerized European audiences. Over the course of the next several centuries, these stories were retold, reinterpreted, and mixed with the stories of others to cement in our imaginations multiple paradigms defining the tropics and the people that lived there. 

<!-- The tropics were either paradise right, Sir Walter Raleigh said that if there's anywhere on Earth, that's as close as there is to the Garden of Eden, it's in the tropics, right? And you see this in both the written word you might see it in artistic works like this painting by Alberta couture was a Dutch painter in Brazil in the late 1600s.  -->

<!-- The alternative, of course, is that the tropics were hell on earth, right? There were health escapes, they're full of disease and dangerous people, they, you know, they were the source of madness.  -->

<!-- You know, recent politicians, at least in the United States, where I live refer to tropical countries in really derogatory ways, in part because this is one of the narratives that they've been hearing for centuries about the tropics, right? Not just about the, the conditions there, but the people that live in the tropics as well.  -->

<!-- I mean, Marco Polo wrote some really beautiful things about some tropical people.  -->

<!-- And then you wrote some really awful things about others.  -->

<!-- And then the third thing that you see is that the tropics, in part, because of these other two things, are our destinations for self discovery, as well as discovery in quotes right of a lot of these natural resources, and about proving oneself.  -->

<!-- That's why people go to the tropics, because either they have this insatiable drive, they can't understand like Von Humboldt, who was just driven and just had to go all the time.  -->

<!-- Or you had daddy issues like Darwin did.  -->

<!-- And the way you proved yourself was by going to the tropics, or you were Teddy Roosevelt, who was frustrated because his political party didn't nominate him to run for president.  -->

<!-- So the way he dealt with that, and got that out of his system, was calling up then Colonel now later Machelle horns on and deciding to explore this tributary in the Amazon that he thought that would be just a really cool way to get over his massive disappointment and not having leadership of the country handed to him.  -->

<!-- And so what you get is the the tropics visited by early Europeans, they come back with narratives about these topics which are consumed by the public and transformed by the public, then share it again in new narratives.  -->

<!-- And ultimately, what you end up is then multiple different versions of what the tropics are.  -->

<!-- And this happened repeatedly and repeatedly and repeatedly.  -->

<!-- And it's happened for centuries and centuries and centuries, to the point where you see these tropes repeated in high art and low art in every aspect of our lives.  -->

<!-- You can trace through these different tropes back to the original writings of people like Sir Walter Raleigh are really Franciscans working through the Americas.  -->

<!-- I mean, if you were to go through high art, it would be Caucasian or Richard Kipling.  -->

<!-- You know, and Fitzcarraldo.  -->

<!-- That's all about proving yourself right, if you want to do instead you know, Tarzan, Eat, Pray, Love.  
<!-- You know, Anaconda.  -->

<!-- This is for me talk about mixed metaphors.  -->

<!-- This is Dolce and Gabbana is 2020 collection, and it's women wild in the jungle, like modern nymphs.  -->

<!-- So we're taking Greek mythology and mixing it with like, generic jungle stuff with a nice smattering of colonialism in there.  -->

<!-- It's, it's just wild, right, and this is this generic interpretation of what the tropics are.  -->

<!-- In fact, the historian David Arnold, who said that, calling a part of the globe, the tropics became a Western way of defining something environmentally and culturally distinct from Europe.  -->

<!-- But also perceiving a high degree of common identity perceiving a high degree of common identity between the constituent regions of the tropical world.  -->

<!-- In other words, it's a way of setting the tropics apart as other while also smoothing over any differences, right? It makes it easier to separate something as distinct when you ignore all the differences that there are within that region that you're considering different from yourself.  -->

<!-- And so you end up over the centuries of this work, reinforcing and manipulating and twisting ideas about what the tropics are, with this kind of platonic ideal of what a tropical field site is.  -->

<!-- And the fact is that this slide has been up for 30 seconds that everybody looks at and goes yeah, this looks like they're trying to figure out where exactly is this place because it looks like an awesome place to go and do some botanizing I think maybe there's one person in the room who realizes that this isn't actually a tropical field site.  -->

<!-- This is Pandora's world of Avatar and Disney World.  -->

<!-- And the reason it looks like so many of the places we work is because that's what Pandora is right? It avatar is really just, frankly, the last rainforest in space.  -->

<!-- This is what they think exotic distant destinations look like.  -->

<!-- They look like the tropics, they look like the places we work, because that's what explorers do, they go to jungles.  -->

<!-- And so the tropics is other and your need became this kind of paradigm for the way we approach the world.  -->

<!-- And scientifically, then that was translated into the biology of the tropics is unique.  -->

<!-- And the same cultural reinforcements about what the tropics were, were absorbed by academics in Europe, and in the United States, who had these ideas in mind when they were formalizing the field of ecology and the field of evolutionary biology, which sets us today, if you have not read this book by Megan rappi, American tropics, it's just a great great reach as a historian at UT Austin, wrote about the Caribbean roots of biodiversity science and how researchers in the United States who were interested in studying biodiversity and understanding why, you know, the origins of biodiversity, then look to the tropics, and decided to establish places in the tropics where they could go do their research and come back and it's worth a read.  -->

<!-- So I'll just use one pull quote from it, which I think is really great, which is that he writes our field is a colonial science.  -->

<!-- Visiting researchers from the United States encountered Panamanians as cooks, or mechanics, writing about what became the Smithsonian, about BCI.  -->

<!-- As cooks, or mechanics, but rarely, as fellow academics, I will tell you this, this is not the case in all of the field stations.  -->

<!-- And this is one of the things that's really interesting is the different ways in which field stations in the tropics operated in different ways in relationship to both local scientists and the scientists that were coming from abroad.  -->

<!-- And so you have this perception of the tropics as different and exotic, and novel and away, right, remote, they were distant, coupled with going and leaving and not interacting with anybody actually, in the tropics when you were there.  -->

<!-- And things like the broader geographical notions of what the world was operating under, you know, this is a typical Mercator projection.  -->

<!-- I've seen several of these in presentations here already in the last couple of days.  -->

<!-- And inside of that is the actual area of countries that are represented there, right.  -->

<!-- And this has come, you know, common among geographers will tell you that the way we see countries in the typical Mercator projection is that a lot of us grew up with reinforced notions of, you know, what countries are big and which ones are small.  -->

<!-- And that translates in many ways, indirectly coupled with his imagery about both the places and the people who live there.  -->

<!-- And so what you ended up constructing was this notion that the biology of the tropics is unique.  -->

<!-- And that means that the tropics are apart, and they can inform our understanding of biology, I've got a stack of articles over there in my backpack from the 40s 50s and 60s, mostly with variance around the title of what the tropics can teach us about biology, right? The tropics are part, there's a biological Foundation, which is really a temperate Foundation.  -->

<!-- And tropical biology is helping to fine tune our understanding of biological systems.  -->

<!-- This is what it means for tropical biology to be specialized.  -->

<!-- There's biology, and then there's tropical biology, which can tell us a little bit about how most biological systems operate.  -->

<!-- And of course, this is, you know, absurd on its face.  -->

<!-- Within the tropics, explicitly defined, right? You have majority of biodiversity, you have roughly 40% of the terrestrial land area, it's not a specialization, it's nearly half.  -->

<!-- The bottom left, you'll see human population by latitude, currently, within the tropics, you have about 43% of the human population just a little more if you're willing to go to about 25 degrees latitude, but by 2025, it's predicted that exactly half the people in the world will be in the tropics.  -->

<!-- And there on the bottom right, is also the emergence of global mega cities of over 10 million people.  -->

<!-- A lot of which will be emerging in the tropics as well.  -->

<!-- Right.  -->

<!-- So it's not that the tropics are other and smaller and narrower and unique, that tropics are actually the foundation right? This is the baseline.  -->

<!-- This is where most of the biology is happening.  -->

<!-- It's where most of the action is it's where at least half the people are.  -->

<!-- And so it's a really useful thought exercise to think about what it would have been like if people's understanding of geography and biology had been just a little bit different if the people who had been setting up the development of our field might have had kind of a more global perspective initially, I think, for instance, this is something that once you once you realize it, you'll start to notice it everywhere.  -->

<!-- What you'll see here is that the people working in the other places, right, the tropics, the specialized include those adjectives in the definitions or in the titles of their articles more often, even even in the highest profile journals, right, which are presumably catering to a broader audience using very broad general underlying principles, right.  -->

<!-- So what second colleagues in this article is why are there so many species of herbivorous insects? In tropical rainforests? We'll get to the formulation of that question in the first place, but in tropical rainforests, whereas Seaman colleagues here working in an old field in Minnesota, right, insect species diversity, abundance and body size relationships, but there's no geography there, right? There's no adjectives.  -->

<!-- And so, you know, in theory, if we'd started from the opposite direction, what you would have seen is that the title of this paper would be why there's so many species of herbivorous insects, and this one would be insect species diversity and abundance, body size relationships in a North American grassland.  -->

<!-- But keep an eye out, you'll start to notice this right? You'll notice this is something at least the postdoc in my lab from Brazil.  -->

<!-- You know, she has pointed out immediately, she said, we're taught to do this.  -->

<!-- But when I came here to the United States, I was really impressed that nobody here does this.  -->

<!-- Right.  -->

<!-- And you can you know, you can have fun with this, if you go backwards.  -->

<!-- And look, you might see that maybe George Stevens, instead of saying the latitudinal gradient in geographic range, have so many species coexist in the tropics, you know, that the title of this paper might have been, you know, the latitudinal, gradient, geographic range, why are there so few species in the temperate zone, right? It's all about the framing, Bob pain foodweb complexity and species diversity, super broad, no geography.  -->

<!-- I mean, let's face it.  -->

<!-- This is a cool paper foundational paper really important to our field, but it probably might have better been titled, surprisingly strong effects of predatory starfish on the modern diversity, food webs of North American tide pools, not as catchy a title, maybe wouldn't have made it into Amnon right.  -->

<!-- Now, if you've heard this before, and I am sure some people have, it's because you probably maybe read this paper from an address to the Panama conference on tropical biology in 1966, by Ripley, who wrote we in the United States are natively a temperate zone oriented people, I'll save you the trouble of reading it all, which is, as a result, in the case of biology, a major part of the accumulated biological, biological knowledge is concerned with a rather minor part of the world fun and flora because of the chance development of biology in the temperate zones.  -->

<!-- This is an old story, we know this, but we keep forgetting it and relearning it, and forgetting it and relearning it.  -->

<!-- And we certainly don't reshape this paradigm.  -->

<!-- The fact is, I mean, I am not advocating I love that word.  -->

<!-- As you'll see in a moment, I think it's actually really important.  -->

<!-- Remember, there's a maybe an A Yes, coming.  -->

<!-- But this adjective, perhaps reinforces the idea that there's biology and the others.  -->

<!-- And in fact, maybe we should be working with our poor unfortunate colleagues who have to work in other places to help them come up with the Association for temperate biology and conservation.  -->

<!-- Because maybe this is the specialized organization that is missing out there that I was looking for.  -->

<!-- So is there really such a thing as tropical biology and I there really isn't, right? If you think about it, it doesn't make sense.  -->

<!-- As a unifying conceptual focus, we transcend disciplines, tools, we try and, you know, we organisms that we study, and really, it's a historical artifact, that's the result of the way in which the history of this world via colonialism operated.  -->

<!-- That's why we think of the tropics the way we do, right.  -->

<!-- It's not the tropics, per se, being clearly defined as distinct, it's because they were formulated as distinct.  -->

<!-- And we were told they were distinct for a really long time.  -->



## 2. Why the answer might be *'Maybe'*

1. Despite its origins as a colonial construct, Tropical Biology could still be a conceptually distinct field if the scientists studying tropical systems address a distinct suite of topics than those working in other regions. 

1. To assess this possibility, I compared the titles and keywords of articles published from 1960-2022 four 'Tropical Journals' (_Journal of Tropical Ecology_, _Biotropica_, _Tropical Ecology_, and _Tropical Conservation Science_) with those of research from both tropical and extra-tropical locations that had been published in six 'General Journals' (_The American Naturalist_, _Evolution_, _Journal of Evolutionary Biology_, _Journal of Ecology_, _Ecology_, and _Journal of Animal Ecology_)  <!-- titles: , Keywords: 1976-2022   -->

2. (N=62,750 and N = 220,612, respectively)
<!-- 1. After downloading the records for these articles from either the Web of Science or SCOPUS, I extracted the titles from all articles and the N = 220,612 keywords from articles published after 1976 using the `refsplitr` package for the R statistical programming language.  -->

<!-- 1. Each article was coded as "Tropical" or "Not Tropical". -->

<!-- 1. I then broke down the titles into Ngrams  -->

<!-- Key Words: frequency analysis -->
I found that 10 of the top 20 key words for articles published in "Tropical Journals" were either a geographic location (e.g., _Costa Rica_, _Amazonia_) or the ecosystem in which the study was conducted (e.g., _tropical dry forest_, _savanna_). 

In contrast, the the 20 most common key words in the "General Journals" were conceptual (e.g., _compeititon_, _species diversity_, _climate change_, _sexual selection_). The exception were articles based on research conducted in the tropics, which also emphasized the location or system. 

The only overlap is in....

Article titles show a similar pattern - the most bi-grams for "Tropical Journals" were almost all about the study system, whereas in Global Journals they were conceptual with three notable exceptions: _Drosophila melanogaster_, _plant/tree species/communities_, and _rain forest_.

_Drosophila melangoaster_ is one of the most important model systems for experimental work investigating evolutionary processes, and plant communities have been a major focus of research since the pioneering work of Clemments and Gleason. Of this work, only tropical forests get a descriptive adjective. 

[@NorthSouthNaming]

While preliminary, this suggests 

<!-- You'll notice at the very top there you have species diversity, biodiversity go figure ecologist and evolutionary biologists are really interested in all these species and where they came from.  -->
<!-- So here we have the top keywords for the global journals, competition, species diversity, climate change, herbivory, sexual selection, dispersal, et cetera.  -->


Discussion & Caveats

<!--So again, we see this being tied to place. The problem is, you could argue that this is because we're studying different things, right? So there really is a difference in what we're studying. But there's a bit of a problem of a kind of a two cannon in the egg here, which is this, right? It could be because there's an interest in studying different things could it could be because when you either are they're preparing an article, you're looking at your research, you think I have to write this up for one of the tropical journals, it's got to be really focused on plays, or this won't get into one of the general journals, because it's not written up in a very general broad way, even if the research is applicable, it's difficult to separate, what we've been taught to think about how to write up research, and what research editors have been taught to think is acceptable for their field, from the actual interest in studying this thing. But one of the things we know about biases and research is in fact that there are these biases based on who's in charge and what people are studying about what they think is most relevant. So I'm gonna leave this as a maybe for now, although I'm pretty sure it's not a maybe.  -->


## 3. Why the answer might be *'Yes'*
<!-- (something that prior prior attempts to define tropical biology often overlooked) (but is this true?) -->
What makes 'Tropical Biology" distinct is not the science _per se_, but rather then broader context in which that science is conducted. Research anywhere can be difficult, but for most tropical biologists the daily struggle with precarious infrastructure, economic volatility, drastically reduced funding for research and education, and political instability can feel insurmountable - and all this is before having to communicate one's results in a foreign language to the potentially biased reviewers [@PeerReviewPerpetuates] and readers of journals that charge open access fees equivalent to several months salary. When added to the physical and emotional toll of disease, crime, working in isolation, field sites being cleared at unprecedented rates, and threats of professional retribution or physical violence, tropical biology and conservation can be uniquely dangerous - even deadly. Lamentably, this is also true for the truly heroic environmental journalists and advocates with whom we collaborate.

## 4. The Future of (Tropical) Biology

How then to resolve this conundrum? I believe that the solution is neither dropping the adjective that inspires so many of us, nor keeping it and accepting status as complementary subdiscipline. Instead, I call on our members to **_reclaim and reshape the Tropical narrative_** by continuing to emphasize what makes tropical biology distinct - place and context - while also repositioning tropical ecosystems as the biological baseline. Here are six simple ways that anyone can contribute to this movement:  

1. **_Cite with purpose._** Citation is a powerful and political act: it conveys legitimacy on the scholarship in the article being cited as well as its author, helps elevate the profile of the author and study system, and those reading your work will cite these articles when writing their own. For many scientists it also plays an important role in their professional advancement. Be mindful of this power and the opportunity it presents when choosing which articles to cite. Cite scientists whose work or approach you feel is undervalued or overlooked. Cite scientists from countries or institutions that have been ignored by the broader scientific community. Cite scientists whose approach to research you feel others should emulate. Cite studies conducted in the tropics.  

1. **_Teach with Purpose._** All tropical biologists are teachers, whether it be in a classroom or in a meeting with policy makers, and teaching also provides an opportunity to elevate the scholarship of others. Be mindful of whose papers are assigned as readings, the studies and systems used to illustrate concepts, the scientists highlighted in presentations, and who is invited to speak in seminar series or present guest lectures. Use your syllabus as a tool to recast the biological narrative about tropical ecosystems and the composition of the scientific community that studies them. Train students in the skills needed when working in tropical systems - collaboration, facilitation, conflict resolution, and communication to diverse audiences [@kainerGraduateEducationFramework2006; @duchelleGraduateStudentsKnowledge2009].

1. **_Collaborate with Purpose._** Helicopter science. International collaboration can be challenging, but the results are often published in more prestigious outlets and have higher citation rates [@smithScientificImpactNations2014]. treating  coauthorship is collaboration. Purposeful collaboration requires    Allow community members to guide the identification of research questions [ @kainerPartneringGreaterSuccess2009]. Push for organizations to strengthen collaborations within the Global South.   

1. **_Build on public fascination with the tropics._** Public fascination with the tropics and their charismatic species [@albertTwentyMostCharismatic2018] provides unparalleled opportunities for outreach and education [@moreiraTamarProjectConservation2017]. Global events like the World Cup [@meloFootballBiodiversityConservation2014], teams with tropical species as mascots [@sartore-baldwinExaminingSportFans2019], movies set in the tropics [@yongReelConservationCan2011], tropical images in fashion [@kuteskoAdidasShowsChanging2014], viral videos about tropical fruits [@SouthFloridaCouple] - we can find creative ways to leverage this universal appeal into support for tropical research and conservation.

1. **_Get in the Game._** It's trite, but true - change requires action. Organizations like the ATBC provide myriad opportunities for meaningful engagement. Help make the process of publishing more fair by serving as a review or subject editor for _Biotropica_. Contribute to capacity building efforts by reviewing student seed grants proposals or serving as a judge for student presentations at the annual meeting. Is there an issue about which you are passionate? Join an ATBC committee or chapter and organize a webinar, workshop, hackathon, or reading group on the topic. What should the Association be doing differently? Tell the leadership at the Council Meetings or stand for election and push for change as a Councillor. 

1. **_Support and celebrate one another_.** Finally, remember that the work done by tropical biologists addresses the "neglected problems that afflict most of the world's people" [@annanChallengeWorldScientists2003] and, regardless of topic, helps advance the socioeconomic condition of the country in which it's conducted. It requires effort and resilience. Seek opportunities to thank and congratulate each other for these contributions -  you're truly making the world a better place.

## Acknowledgments


## Disclosure Statement

The author confirms that there have been no involvements that might raise the question of bias in the work reported or in the conclusions, implications, or opinions stated.


<!--- really proud of ourselves. One, thanks a lot, especially with the university. They just wonderful partners. And, you know, I will tell you that Harvard, although it was officially founded in 1636, they were only incorporated in 1658. So your head of Harvard. -->
<!-- Thank you very much, Emilio for your great talk. Now we're open for questions. We have time for one or two. -->
<!-- I knew it said that thing about -->
<!-- patchy later. But fascinating talk really interesting. Over the last decade or two we've got used to not using the highly inappropriate term developing countries and using the global south as a term. And for basically what you're saying is the global tropics are much better term. And the global south is a problem as well, that Australia and things is a global tropics, a better concept and global South, actually. So othering the tropics and actually enhanced -->
<!-- global Tropics might be more appropriate. I don't think I think most people who think so there is no perfect term. That's part of the problem. But I think a lot of the people I've had interactions with who find the term global south most problematic haven't actually read the report that generated that, you know, from whence that term came, all of which explains, you know, it's about the flow of commerce and economic power. It's a you know, the term global south reflects the colonial and economic history. It's not just geography. And so global Tropics might be really reasonable, although, of course, that excludes a lot of the Southern Cone and other places that you know, as well. So I, I don't think there is a perfect term. And this is one of those arguments where you can no matter what term you use, you might make 80% of the people happy and 20% will be your reviewers. And so I'm not sure what the solution is. I really do want to emphasize though that I don't think it's a bad adjective, right? People. People really aren't passionate about this adjective, and they have been for a long time this painting by church In 1859 13,000 people filed by this painting, they paid a quarter each in the 1850s. To file by this painting, called the heart of the NDS, and look at it for a moment in a museum. There were lines around the block. People are fascinated by these systems. Why on earth we do away with this term, I think we need to play on it. Whether we use it as a unifying theme for how we think about socio economic development, or as a rallying cry for conservation or, you know, code switch and use it when we need to. I'm not really sure, but there's no way we should be getting rid of this adjective anytime soon. -->
<!-- Does anybody else have a question? Oh, yep. -->
<!-- I've heard you yell, my yellows. I can hear you from here. -->
<!-- Thank you interview for the fifth inning. -->
<!-- Now that's somebody else. If somebody else has a question, she gets to go first. Just because you grabbed the mic. If it's if it's Lawrence, who has a question, that's fine, but I heard my loss. And that's like, seriously, dude, come on. We just had to talk about colonialism. -->
<!-- I'm just servants both at home and Okay, go ahead. Go ahead, Lawrence. Yeah, so I had this, as a student have the choice to go to a boring Dutch beech forest, or a fascinating tropical forest. So I went to this fascinating tropical forest. And I lived in this small town called river otter, which is in the periphery of where you can think, where you can be in Bolivia. So I had a feeling it was at the end of the road on the set, you're getting off the wheel, that's where it starts. But I realized that leaving everybody on time, it's your very far away from Santa Cruz. And thereafter people feel that they are marginalized, because the center of the power is in the past. So for me this whole story, you tell the story about center versus periphery. So what could be the role of global leaders in the south like Brazil, like Mexico, and leading Institute's like blue num, and like the USVI in democratic making science more democratic, also within their countries and connecting, for example, to Africa? -->
<!-- Yeah, that's a really important point, actually, in this paper, by stocks at all, we, when we reviewed the work, there's a clean distinction in the way that countries operate. It's the one that gave this result here. Brazil and Mexico actually are the ones where most of the work being done in that country is being led by scientists from that country. You know, Costa Rica, Panama, those are some of the ones where it's people from outside coming in. So I think leading by example, is a really good idea. Right, one of the Brazil's a highly productive scientific community that in many cases doesn't, you know, it doesn't need to go outside, right. But I do think that there is a way for people to do this. See if I can pull that map up. -->
<!-- That that is what they can do. If you notice, there's one of the things about for instance, Brazil, which is one of the case studies that I've studied. Brazil has very little collaboration in house across institutions. Most of the collaborations there are between that some Paulo, Eugenia miniaturize section. And outside the Europe or the United States, there's a lot, a lot less productive collaboration with other institutions in Brazil, and almost none across the tropical South, right, the global tropics. And so I think that, in many cases, scientists in this country are doing exactly the right thing. They're creating great graduate programs doing great research, it's cutting edge, they're sending it off to the best journals possible. But then acting as leaders means looking to collaborate and capacity build across the south instead of internally, via collaborations externally with the Global North. That that that's the missing piece right there. For me, there are no this isn't actually a map, right? Each point represents a co authorship location, it's done by someone else. It's great map. But there are no lines defining political boundaries in this map. And there, it's you can see individual places, but there aren't a lot of lights in in a place where there is a lot of land. There are a lot of people and there are a lot of universities. And that's unacceptable. -->
<!-- All right. Emilio. Oh, -->

<!-- John, bring it there's -->
<!-- there's a debate to this that deserves Spencer, though. I'm an old timer, who's seen a lot and started in my tropical biology career back in the early 1962. And as you know, I was in Peru practically all that time. But when I started in Peru, there was no Ph. D program in the country. The professor's in the universities there had bachelor's degree only or maybe as sort of the sense yet thorough, it was a little beyond that. And there was no career path in biology. There was nothing happening. There was no future there was no possibilities for students and A lot has changed. It changed enormously. And now there are scores of Peruvian PhD biologists, a lot of them are scattered all over the world, some of them in this room. And that makes collaboration so much more natural and satisfying. The intellectual level between people from US Europe and their southern counterparts is, is on a level playing now, it was never that before. So I think things have improved hugely in over my lifetime. Yeah, -->
<!-- I'm glad to hear that. And I think one of the one of the things that stands out is in a lot of places, individuals play a really key role, right. So, you know, in Mexico, a lot of us would probably point to the arrival of the return of horses that have come from Wales as being a really key moment in the development of ecology in Mexico, for instance, right, or the arrival of someone who commits to a lifetime. I'm working in Peru and training students and bringing people along, that's really great. I can't emphasize enough how much that those interactions pay off. One of the things I didn't show in this literature review is I actually went and looked to see when someone based in a different country appeared for the first time in the journal ecology, for instance, you know, ecology has been publishing since the early 1900s. There was an American who fought. That's why I mentioned to candidates, he was an taxonomist, who fought with all the taxonomies here and he left the country, he was kind of a vagabond, really interesting character, he left and he published two papers when he was in Brazil before he moved off to another country. So he appeared there, but in the journal ecology, not that there weren't Brazilians, they may have been outside in institutions outside the country. But there wasn't a paper with a Brazilian address on it, you know, primary address until the 1980s, at which time there were two, throughout the entire decade, people based at a Brazilian institution with a paper in ecology, a couple of those were actually expats who moved there. In the 1990s, the entire decade, there were a total of nine papers with the Brazilian author home address on them in the journal ecology, there are people in this room have published, like, yet vendors published like nine papers in ecology, like in the last 20 minutes, right. And so this, this is think about what this means to the intellectual development, the very thing you're talking about, you know, people in my lab, or you had vendors lab can turn around and get advice on how to submit a paper to one of these journals, or how to write a paper for one of these journals, from the person in the next next desk, or next office or down the hall, you know, for an entire day. I mean, if you were in a country like this for an entire decade, there was no one in the country you could turn to, to get some basics about like, hey, easily. What do you think, do you think this would be good for college. And so when you jumpstart that, of course, Brazil is now up to 20 in a year, but you jumpstart, and that's the hard part is finding how you go from where you started to what you see now. And I put weight on individuals, individuals, I think, are far more powerful than they think. Despite what feels like just the overwhelming pressure of everything that's going on around us. You can start small site Well, and, you know, site site with, you know, purpose, and teach with purpose. And I think that's really a great way to get started. And I see what needs to get us rolling. Yep. And I shouldn't just say one, our organizers need to get us started. -->


\newpage

# References


::: {#refs custom-style="Bibliography"}
:::





```{r fig1, fig.align="center", out.width = "100%", fig.cap='(A) Tropical biology conceptualized as biological specialization. (B) Tropical ecosystems conceptualized as "unique" or "special".'}
p1 <- ggdraw() + draw_image('./manuscript/figures/Slide1.jpeg', scale = 1)
p2 <- ggdraw() + draw_image('./manuscript/figures/Slide2.jpeg', scale = 1)

plot_grid(p1, p2, labels="auto", greedy=TRUE)

```

```{r fig2, fig.align="center", out.width = "100%",fig.cap='Alternative ways in Biologists self-organize into specialized subdiciplines: (A) the Conceptual Domain from which they approach their work, (B) their focal Study System, and (C) the Methdological Approaches they use to conduct their research.'}
p1 <- ggdraw() + draw_image('./manuscript/figures/Slide3.jpeg', scale = 1)
p2 <- ggdraw() + draw_image('./manuscript/figures/Slide4.jpeg', scale = 1)
p3 <- ggdraw() + draw_image('./manuscript/figures/Slide5.jpeg', scale = 1)


plot_grid(p1, p2, p3, nrow=1, labels="auto")

```
